\documentclass[11pt]{article}
\pagestyle{plain} \topmargin -.5in \oddsidemargin 0in
\evensidemargin 0in \textwidth 6.5in \textheight 8in
\setlength{\parindent}{0in}
\begin{document}
\section{An AMAZING study break on your floor}
Emily Guthrie
\newline
Starting Bid: \$30
\newline
If icing your own cupcakes, capture the flag, or anything fun is an interest to you, you should bid on this item. Get together with your floor mates and bid on this and I'll do whatever you want or meet your wildest dreams.
\newline
\newline
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid~~~~~~~~~  & ~~~~~~~~~~~~~Email Address (if different name or not standard olin.edu)~~~~~~~~~~~~~\\
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
\end{tabular}
\newpage
\section{Resume}
Sally Phelps
\newline
Starting Bid: \$25
\newline
Sally will write a fantastic resume for you FROM SCRATCH!
\newline
\newline
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid~~~~~~~~~  & ~~~~~~~~~~~~~Email Address (if different name or not standard olin.edu)~~~~~~~~~~~~~\\
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
\end{tabular}
\newpage
\section{Romantic Date for Two hosted by Chef Coppola and Mr. Reznik}
Adam Coppola and Michael Reznik
\newline
Starting Bid: \$20
\newline
Surprise your loved one by inviting them to this romantic dinner for two in Olin's premier dining spot, complete with a breath-taking view of the Olin campus, a spaghetti dinner cooked up by Chef Coppola, and, most importantly, some classic, mood-setting piano entertainment by Mr. Michael Reznik.
\newline
\newline
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid~~~~~~~~~  & ~~~~~~~~~~~~~Email Address (if different name or not standard olin.edu)~~~~~~~~~~~~~\\
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
\end{tabular}
\newpage
\section{Make Your Own Beverage}
Allen Downey
\newline
Starting Bid: \$50
\newline
Make your own 5-gallon batch of beer, cider or mead! You pick a recipe, then I shop for ingredients.  You and up to 3 friends come to my house to make a batch, sample related styles, and perhaps dip into my supply of mysterious unlabeled leftovers! Two weeks later, you all come back to put the batch in bottles. Beer is ready 4-6 weeks later; cider and mead take longer.  All participants must be 21 on brew day.
\newline
\newline
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid~~~~~~~~~  & ~~~~~~~~~~~~~Email Address (if different name or not standard olin.edu)~~~~~~~~~~~~~\\
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
\end{tabular}
\newpage
\section{Wings and Football}
Brian Storey
\newline
Starting Bid: \$50
\newline
Wings and Football.  

I will take up to 6 people out for as many wings as you can eat to watch the football game (or other sporting event) of your choice. Reasonable amount of beverages included for those 21+.  
 


\newline
\newline
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid~~~~~~~~~  & ~~~~~~~~~~~~~Email Address (if different name or not standard olin.edu)~~~~~~~~~~~~~\\
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
\end{tabular}
\newpage
\section{Lunch with the Museum of Science President and 2 Exhibit Hall passes}
Beth Miaoulis
\newline
Starting Bid: \$40
\newline
One of the world's largest science centers and New England's most highly attended cultural institution, the Museum of Science is a leader in the national effort to promote engineering education awareness, bringing science, technology, and mathematics alive through its exhibits, programs, and more.

You and a guest can enjoy the exhibit halls and have lunch with the museum's president and director, Yannis Miaoulis. He can share with you his passion for engineering education and hands-on museum learning experiences, and you can share you passions and Olin's do-on learning environment.

\newline
\newline
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid~~~~~~~~~  & ~~~~~~~~~~~~~Email Address (if different name or not standard olin.edu)~~~~~~~~~~~~~\\
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
\end{tabular}
\newpage
\section{Man Hall serves you dinner}
Man Hall
\newline
Starting Bid: \$100
\newline
The bodacious men and women of Man Hall will serve you a full three course dinner at the dining hall. If the bidding gets over $200, we'll do it in our Dirndls.
\newline
\newline
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid~~~~~~~~~  & ~~~~~~~~~~~~~Email Address (if different name or not standard olin.edu)~~~~~~~~~~~~~\\
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
\end{tabular}
\newpage
\section{TOSCANINI'S}
The FACULTY
\newline
Starting Bid: \$50
\newline
Ice cream is good. Tosci's is the best. Ten people. Each picks a pint. You pick the day. We buy it. We bring it to the dining hall. We sit amidst all of those without and they envy our ice-cream induced bliss. Bid and enjoy edible bliss.

Love,
The FACULTY

\newline
\newline
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid~~~~~~~~~  & ~~~~~~~~~~~~~Email Address (if different name or not standard olin.edu)~~~~~~~~~~~~~\\
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
\end{tabular}
\newpage
\section{Outlets Outlets Outlets!}
Jessica Townsend
\newline
Starting Bid: \$50
\newline
Want to update your wardrobe? Looking for a new style? I'll act as personal shopper for a group of up to 5 people. I'll chauffeur you in style to the Wrentham Outlets and we'll spend the day shopping for bargains, trying out new styles, and generally having a good time. I'll splurge for lunch to keep our shopping energy up.
\newline
\newline
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid~~~~~~~~~  & ~~~~~~~~~~~~~Email Address (if different name or not standard olin.edu)~~~~~~~~~~~~~\\
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
\end{tabular}
\newpage
\section{An airplane!  With flying lessons!}
Drew bennett
\newline
Starting Bid: \$25
\newline
A ParkZone Mini Vapor RTF model airplane. Suitable for flying indoors (hallways, rooms, gyms, etc) or outdoors in calm weather.  Comes complete with transmitter!

I will also give the proud new owner some flying lessons if they wish it!

\newline
\newline
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid~~~~~~~~~  & ~~~~~~~~~~~~~Email Address (if different name or not standard olin.edu)~~~~~~~~~~~~~\\
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
\end{tabular}
\newpage
\section{Dinner at Chez Somerville}
mark somerville
\newline
Starting Bid: \$50
\newline
You and five of your closest friends will experience the culinary delight that is Chez Somerville.  A four course gourmet evening, complete with age-appropriate accompanying beverages, can be yours -- if the price is right... Scintillating and/or embarrassing/awkward conversation with the Somerville family is entirely optional.  
\newline
\newline
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid~~~~~~~~~  & ~~~~~~~~~~~~~Email Address (if different name or not standard olin.edu)~~~~~~~~~~~~~\\
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
\end{tabular}
\newpage
\section{Olin Takes Over the Under Bones}
Paul Ruvolo
\newline
Starting Bid: \100
\newline
Join Olin faculty and staff in enjoying some of Boston's best barbecue and beer at Redbones Barbecue!  Redbones is a Somerville institution located in the heart of Davis Square.  This event has a lot of interest on the faculty / staff side (final list of participants pending, but it is going to be awesome).  We are hoping to get a large group of students to bid on this item so that we can reserve the entirety of the "Underbones" (the dimly lit, funky, lower-level of Redbones).

Restrictions:
You should be 21 if you intend to drink (absolutely no exceptions)
Maximum of 30 students (due to space constraints).

Logistics:
We will have to schedule this event several weeks in advance to ensure that we can reserve all of the Underbones.
\newline
\newline
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid~~~~~~~~~  & ~~~~~~~~~~~~~Email Address (if different name or not standard olin.edu)~~~~~~~~~~~~~\\
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
\end{tabular}
\newpage
\section{Win the SERV Auction}
Bill Warner
\newline
Starting Bid: \$5
\newline
You win the 2013 SERV Auction! Complete with certificate of authenticity signed by relevant parties.
\newline
\newline
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid~~~~~~~~~  & ~~~~~~~~~~~~~Email Address (if different name or not standard olin.edu)~~~~~~~~~~~~~\\
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
 & & & \\
\hline
\end{tabular}
\newpage
\end{document}
