\documentclass[11pt]{article}
\pagestyle{plain} \topmargin -.5in \oddsidemargin 0in
\evensidemargin 0in \textwidth 6.5in \textheight 8in
\setlength{\parindent}{0in}
\title{Silent Auction Donation Packet}
\author{SERV Auction 2015}
\date{November 9th, 2015 to November 13th, 2015}
\begin{document}
\maketitle
\section{Business Donations}
\subsection{Be a part of the magic!!}
TRIUMVIRATE OF SHADOWS
\\
Starting Bid: \$1
\newline
You don’t know what you’re bidding on.
But it's related to The PENULTIMATE Treasure Hunt.
\subsection{2 Metallic tattoo stickers}
Red Apple Convenience 
\\
Starting Bid: \$2
\newline
Some shiny temporary metallic tattoos. They look cool!
\subsection{Edgy Rocksbox jewelry}
Rocksbox
\\
Starting Bid: \$5
\newline
\$250 worth of jewelry - you can wear each piece in this edgy set on its own or together!

Gorjana Mila Shimmer 3 Ring Set in 18k gold plating with white cubic zirconia, size 7, retails for \$98
8 Other Reasons Glory Earrings, retails for \$20
House of Harlow Sunburst Bangle in Black and White, retails for \$68
SLATE Spectrum Necklace, retails for \$68

All jewelry has been previously worn but it is good condition :)
\subsection{Modern chic Rocksbox jewelry}
Rocksbox
\\
Starting Bid: \$5
\newline
\$250 worth of jewelry, each modern chic piece can be worn on it's own or you can wear them all together!

Perry Street Lina Necklace, retails for \$75
Gorjana Mave Shimmer Double Studs, cubic zirconia detail, retails for \$45
Margaret Elizabeth Faceted Cocktail Ring in Aqua Chalcedony, sterling silver hand dipped in 24k gold w/ semi-precious stone, size 5, retails for \$118
Gorjana Sea Stripe Bangle in Navy, polished enamel in a nautically inspired pattern set in 18kt gold plate, retails for \$100

All pieces are used but in good condition :)
\subsection{Tour the Rocksbox office!}
Maia / Rocksbox
\\
Starting Bid: \$5
\newline
In San Francisco Bay Area. Come tour either the Rocksbox fulfillment warehouse or HQ... or, if you move FAST, you can see both. Previous visitors have said that it's "not that bad". If you come to the warehouse you will get to pack a box for a customer, learn the Rocksbox way to tie a ribbon, and see how the whole process works -- and you can ask questions about how it's evolved.
\subsection{\$20 to Truly Yogurt}
Truly Yogurt
\\
Starting Bid: \$5
\newline
Frozen Yogurt and Ice Cream for days (well, like 5 days, but you get the idea).
\subsection{\$30 Gift Certificate}
Wasik's 
\\
Starting Bid: \$10
\newline
Do you like cheese? Of course you do. What about, like, good cheese? Yes? Perfect. Win this item. Get Cheese.
\subsection{\$30 Cafe Mangal }
Cafe Mangal
\\
Starting Bid: \$20
\newline
Cafe Mangal is quaint BYOB luring locals with a menu of Turkish-inspired Mediterranean fare \& homemade desserts. Fantastic food, relaxed atmosphere.

"Feels like one of those very nice, but posh, open-air Turkish Cafes, but I have no idea what I'm talking about"- Dhash
\subsection{\$60 gift certificate, for A haircut \& Style \#1}
Richard's of Wellesley
\\
Starting Bid: \$30
\newline
Richard's of Wellesley is as super nice haircut and stylist place. They're super nice and it looks like they give great haircuts. +1 would reccomend
\subsection{\$60 gift certificate, for A haircut \& Style \#2}
Richard's of Wellesley
\\
Starting Bid: \$30
\newline
Richard's of Wellesley is as super nice haircut and stylist place. They're super nice and it looks like they give great haircuts. +1 would reccomend
\section{Arts and Crafts}
\subsection{Be Adam for a day}
Adam Coppola
\\
Starting Bid: \$0
\newline
Ever wanted to be someone beside yourself?
Specifically, ever wanted to be Adam Coppola?
Be the winning bidder on this item and you will receive step-by-step detailed instructions on "how to be Adam Coppola" for a full day. I'll spend some time coaching you, then you'll take yourself on this very other-personal journey.Contact me with any questions.
\subsection{Chainmail bracelet}
Emily Tumang
\\
Starting Bid: \$0
\newline
A handmade bracelet made of aluminum.
\subsection{I will crochet you a thing}
Charlie Weiss
\\
Starting Bid: \$0.5
\newline
I will CROCHET you a thing. To be perfectly clear I will NOT be KNITTING you a thing.

Quality of piece directly correlates to amount of bid. 50 cents will get you a pile of yarn. 50 more cents will get you a braided pile of yarn. 5 dollars could be a cute small animal. 15 dollars could be a pretty cowl. 100 bucks and I will make you a lovely blanket.

Tell me what you want and I will tell you if it is feasible, and an approximation I can do if it is not. Larger pieces take more time for obvious reasons.
\subsection{Hand-made Elephant Mug from India}
Kelly Brennan
\\
Starting Bid: \$1
\newline
In Pondicherry, India, artists make beautiful pottery! My personal favorite is the mug where the handle is in the shape of an elephant head. The trunk forms the mug handle! There is a large collection of these mugs just down the street from me. I will bring you a hand-made elephant mug! If bidding goes above \$15, I'll give my best attempt at making Indian Chai and serving it to you in the mug.
\subsection{Custom Origami Model}
Evan Dorsky
\\
Starting Bid: \$1
\newline
I do Origami (paper folding). I will make you Origami! Some of my favorite categories:

- Animals (birds, bugs, mammals, etc.)
- Flowers
- Geometric (modular) sculptures
- Your favorite category!
\subsection{Tie-Dye PowerChords Shirt}
PowerChords
\\
Starting Bid: \$1
\newline
Did you know.....that PowerChords has an unused secret collection of white PowerChords t-shirts? We will make you the special edition tie-dye PowerChords t-shirt of your dreams if you bid on this item. Become the ultimate Olin a cappella \#1 fan with this swag of legendary proportions.
\subsection{1 second of my life}
Shane Skikne
\\
Starting Bid: \$1
\newline
I take one second of video everyday and combine them into a video of my life! Come January, I will have been doing this for 3 years. You get to be my second (or choose my second) on the day you choose.

Above \$3 and you can get 1.5 seconds!
For each multiple of \$5, you get an additional day (though, now I get some say on which days you choose)!
\subsection{Collected Works}
Caleb Kissel
\\
Starting Bid: \$1
\newline
Over the years, I have written a few silly poems about events and people in Olin's history. I have found eight of them. None of them are new, so you've probably seen them, and some of them might not make sense if you aren't a senior, so be warned. Finally, these are works of fiction and any illegal activity depicted herein is for artistic purposes only; any resemblance to real people or events is certainly coincidence. That said, if a staff member purchases this, all names will be censored.

If the bidding reaches 8 dollars, I'll put them in a binder and write an artist's statement for each work.
\subsection{Knock off Stolk Pottery}
Saarth
\\
Starting Bid: \$1
\newline
I will make you a piece (cup, bowl, mug) of pottery of your choosing. It will not be as good as anything that Stolk every made, but I promise to be motivated.
\subsection{Custom Origami Instructions}
Lydia Z.
\\
Starting Bid: \$1
\newline
Have you ever been tempted to lovingly sculpt Shia LeBoeuf's head from a sheet of paper? *
...Do you suck at origami?
Then this prize is for you!

You'll receive:
\textgreater A fold-by-fold set of instructions to whatever origami figure you choose
\textgreater One completed demo model
\textgreater Lots of origami paper

Any figure is possible- not just cranes, etc. This doesn't have to be an origami design that exists already.

(*Cannot guarantee close resemblance to Shia. We'll do our best.)
\subsection{Electronic Jewelry}
Lydia Z.
\\
Starting Bid: \$1
\newline
Take your relationship with circuits to the next level!

I will create one piece of jewelry out of resistors, LEDs, and suchlike.
Perfect for Christmas presents.
If bidding reaches \$5.00, I will make the jewelry out of a functioning circuit of your choice. (Batteries not included.)
\subsection{An interesting poster}
Adit 
\\
Starting Bid: \$1
\newline
I'll make you an interesting looking poster. It will be really professional looking.
\subsection{A print}
Adit
\\
Starting Bid: \$1
\newline
I have some interesting looking prints from lithography last year. You can have one. Maybe I'll put it in a frame.
\subsection{I'll Draw You a Picture}
Devynn Diggins
\\
Starting Bid: \$1
\newline
I'll draw something of your choice! I usually work in ink but I have some limited experience with watercolors if you want something that isn't black and white. Higher bids mean more complicated pieces.
\subsection{Custom Friendship Bracelet}
Rebecca Jordan
\\
Starting Bid: \$1.5
\newline
I make knotted friendship bracelet exactly as you want it! If you don't have something in mind, I'll help you design an awesome-looking pattern. I can do patterns, letters, pixel art, and almost anything you can design on a grid. The higher the bid, the wider the bracelet you can design.
\subsection{Join the Onshape SCOPE team on a collaborative Onshape document, and experience the madness}
Amanda Sutherland
\\
Starting Bid: \$2
\newline
Description: We will set up a time and date, and then we will have a CAD free for all. It’s like a google doc disaster, but better because it’s CAD. No knowledge of CAD/3D modeling required. Mouse can be provided. *
Our SCOPE advisor, the fantastic Ben Hill, will be adding his wisdom as well.
*probably not a live one
\subsection{Glass Bead(s) or Marble(s)}
Jayce Chow
\\
Starting Bid: \$3
\newline
Pick one or two colors and I will make you a glass bead or marble (your choice). The higher the winning bid, the more complex of a design I'll do. You also might get more input in what it looks like/you might receive more than one bead/marble.
\subsection{Handwritten letter}
Ilana Walder-Biesanz
\\
Starting Bid: \$5
\newline
Need to thank someone in an elaborate manner? Need to write an impressive love letter? Simply feeling lonely? I will write a letter for you in fountain pen on cotton paper and seal it with wax! There are two ways this can go---you can give me a message to write out in my most elegant cursive, or you can just ask me to write a letter to you (with whatever content comes to mind). Either way, it will be the prettiest piece of mail you or the recipient has ever gotten.
\subsection{Handspun yarn}
Kathryn (Rivard) Mazaitis
\\
Starting Bid: \$5
\newline
Are you a knitter or crocheter? Have you ever searched a yarn store top to bottom and found it lacking? Or perhaps you like the idea of working with yarn someone made with their actual hands on old-school spinning equipment? This listing is for you!

I spin fiber (wool, alpaca, silk, or blends) into yarn (singles, 2-ply, 3-ply, chain-ply, or opposing-ply[great for socks; can't buy it in a shop]) on spindles and spinning wheels. I can do smooth yarns or slubby yarns, single or multicolored, plain or sparkly. I can do anything from a heavy laceweight/light fingering up to super-bulky. I can even dye something up for you with plant-based dyes.

You'll get 4oz of yarn spun to your specifications, from fiber in my stash (yardage varies by fiber and yarn diameter). If bidding exceeds \$20 I'll add in another 4oz, and again for every \$15 thereafter.
\subsection{Custom Glass Bead}
Jiaying Wei
\\
Starting Bid: \$5
\newline
I make lampworked glass beads, if you bid on this item I'll make you a custom glass bead (you can either choose the theme or let me go wild), if bidding goes over \$20 I'll turn it into a necklace/bracelet/jewelry item of your choosing.
\subsection{Butt drawing/painting}
Ruby Spring
\\
Starting Bid: \$5
\newline
Depending on what you want and how much you pay, I will create a visual interpretation of your butt. This could be a "simple" drawing using whatever medium makes sense (colored pencil, charcoal, graphite, oil sticks, etc) but could be as elaborate and prestigious as an oil painting worthy of you mantelpiece. Photographs excepted, though I do prefer live models.

If you doubt my abilities to make your butt look just the way it is or otherwise, here's some of my portfolio: http://visualartsupplement.blogspot.com/
\subsection{Print You Something Awesome}
Alexander Crease
\\
Starting Bid: \$5
\newline
I 3D print lots of really crazy things. I will print something crazy specifically for you!
\subsection{Digital Illustration of That Thing You Love}
Antonia Elsen
\\
Starting Bid: \$5\$
\newline
Custom digital illustration (painted in photoshop) of whatever you want. Can easily be printed out as sticker or poster.
If you want an example of what I can do, hmu.
\subsection{Design and create a board game for you}
Connor Stokes
\\
Starting Bid: \$5
\newline
I will design a board game based on your input and create a copy of it so you can play it with your friends.

You tell me:
What genre of game is it? 
Abstract strategy, German style, card game, deck building, micro game, etc. 

What's it about thematically?
Working at a movie theater? Running for office? Growing and selling tulips? UOCD? Anything you like, even if it's an abstract strategy game.

How many players should it be designed for? 1? 2? 10? Anywhere in between or beyond? Up to you.

Based on that input and maybe a few further questions, I will design the game and produce a physical copy of it for you. I can't guarantee it will be balanced or fun, but I'll give it my best shot.
\subsection{Screen Printed Poster }
Saarth and Doyung
\\
Starting Bid: \$5
\newline
You can get yourself a Doyung and Saarth original screen printed poster. Over \$25 and we will make it a four color print.
\subsection{Themed Pillows}
Cecelia and Annabel
\\
Starting Bid: \$5
\newline
We will each make you a pillow (totaling to 2) on a theme/s of your choice.
\subsection{Donut Pillows}
Cecelia and Annabel
\\
Starting Bid: \$5
\newline
We will each make you one pillow that looks like a frosted donut.
\subsection{Hand woven copper bracelet}
Claire Kincaid
\\
Starting Bid: \$10.00
\newline
Hand Woven Copper Wire Bracelet, designed and fabricated by me
\subsection{Write You A Newsletter}
Forrest Bourke
\\
Starting Bid: \$10
\newline
I'll write you a newsletter. You don't get a lot of say over the content. You can ask Aaron Hoover if he's satisfied, he won this item last year.
\subsection{Fill a room with balloons}
Maura
\\
Starting Bid: \$10
\newline
I will blow up enough balloons to completely fill a room. It could be your room, it could be someone else's room. Pick a room and I will fill it with balloons.

For 10\$ I will fill one persons room with balloons.

For every additional 15\$ I will fill another room.

If it gets to 50\$ I will fill a lounge with balloons.
\subsection{Calligraphy Snail Mail}
Lindsay Gordon
\\
Starting Bid: \$10
\newline
I graduated in 2007, currently live in San Francisco and have worked at Google for 5.5 years. I recently fell in love with calligraphy and need some new people to send calligraphy addressed snail mail to!

I'll send you 3 cards with beautifully written/decorated envelopes. I'm happy to tell you about San Francisco adventures, any interesting classes I'm taking, my favorite stories from Olin or anything else that intrigues you.
\subsection{Cardboard Furniture }
Lauren Froschauer
\\
Starting Bid: \$10
\newline
I will make you a custom piece of cardboard furniture. Coffee Tables and Shelves are my specialties, but I am up for anything! 
The more you pay, the fancier it gets!
\subsection{Packet of 10 Cards Handmade by Kolkata Slum-dwellers}
Philip Z Loh
\\
Starting Bid: \$10
\newline
For supporting Feed India, I obtained a packet of 10 beautiful cards handmade by poor people who live in the slums of Kolkata, India. You can now amplify the philanthropic work possible with these cards by winning them and donating the proceeds to another charity. These are the cards that keep on giving.

Cards made out of rice straw. They look exquisite and unique!
\subsection{Hand-made Jewelry, or "The Jewelry that Keeps on Giving"}
Philip Z Loh
\\
Starting Bid: \$18
\newline
I just won a jewelry-making class at the Microsoft Auction (similar to the SERV Auction) for \$53. I'm now donating the end-product of that class to the SERV Auction to amplify the good that can come out of this.

I'll do my best to make it/you look good! \textless 3
\subsection{Print you something awesome}
Claire Diehl
\\
Starting Bid: \$20
\newline
I print lots of really crazy things. I will print something crazy specifically for you! This is relief printing which involves carving or drawing a design and printing it repeatedly in ink. \$20 is a set of ~5, ~4"x6", 1 color prints of imagery of your choice (with artistic licence). Number, size and colors can be negotiated based on donation.
\subsection{Magneto helmet / make you a helmet}
Maura
\\
Starting Bid: \$20
\newline
I will gladly make you one of Magneto's famous telepathy blocking helmets, you get to choose which design!

If the bidding goes over 40 dollars, I can work with you and attempt to make you another type of helmet.
\subsection{Handcrafted cards with my photography}
Lindsay Gordon
\\
Starting Bid: \$20
\newline
I graduated in 2007, currently live in San Francisco and have worked at Google for 5.5 years. I love photography and enjoy printing out my photos, making them into cards and giving them to friends and family as gifts.

I'd like to let you choose ten of my photos, I'll print them out and mount them on cards for you and you can treat your friends and family to some handmade snail mail. Check out some example photos at lindsaygordon.com/photography
\subsection{Hand Dyed Napkins - Set of 6}
Jenn Simonovich ('12) and Celeste Maisel ('13.5)
\\
Starting Bid: \$20
\newline
Jenn Simonovich ('12) and Celeste Maisel ('13.5) will make you a hand-dyed set of six cloth napkins! These will be hand-dyed, one of a kind, completely unique napkins sewn and then dyed by us in our San Francisco backyard (if you're local, you can even join us on Dyeing Day). You can choose between natural, plant based dyes or modern chemical dyes, and we'll work with you to help figure out patterns and colors. For every \$10 over the starting bid, we'll add two more napkins. If the bidding hits \$60, we'll include a hand-dyed tablerunner. If bidding reaches \$120, we will even add a full-sized tablecloth.
\subsection{Yarn Stash Starter}
Joles
\\
Starting Bid: \$25
\newline
Designer yarn valued at no less than \$50. Winning bidder and I can discuss preferences before I pull from my stash. I have mostly natural fibers in muted colors, and some high end novelty yarns. I'll throw in pattern books if I have them for the yarns you pick.

I have a small selection of yarns not commercially available, or in colors that were never sold. 

Some of my stash is up on Ravelry (failjolesfail) if you want to take a look.
\section{Events}
\subsection{Chats with a z at the end and a nap at the end}
Annabel and Cecelia
\\
Starting Bid: \$0.5
\newline
The more you bid the less we will talk.  Also we will take a nap (zzzz).

**This is not a service but an event.
\subsection{Quality time with FRIENDS}
Inseong and Abi
\\
Starting Bid: \$1
\newline
Spend quality time watching the best TV show ever and doing a black/white friends puzzle. (High quality beer provided for 21+)
\subsection{Indian Indian Walk}
Rahil, Saarth, Ankeet, and Adit
\\
Starting Bid: \$1
\newline
We'll provide the fire, you provide the balls
\subsection{Pun War}
Alexander Crease
\\
Starting Bid: \$1
\newline
I challenge you. To a battle of the champions. Your weapon? The lowest form of humor. Bid if you dare.
\subsection{Double Adventure}
Alexander Crease
\\
Starting Bid: \$1
\newline
Double dates are for squares. Come on a double adventure! It will be fantastic. Absolutely fantastic.
\subsection{You get to have lunch with me}
Brian Liebson
\\
Starting Bid: \$1
\newline
I'll eat lunch with you...or rather you get to eat lunch with me. For every \$1, I'll eat lunch for 20 minutes.
\subsection{Parcel B Tour}
Anne LoVerso \& Michael Sheets
\\
Starting Bid: \$2
\newline
Hidden in Parcel B are such items as: 3 cars, in various states of decay, a bag of bones, something like 7 fire pits, and more!  We won this last year, it's is our duty to pass it along this year and show you what we learned
\subsection{TV Marathon}
R2 Team
\\
Starting Bid: \$2
\newline
Watch an episode of your favorite tv show in Annabels room with at least half R2's
\subsection{Watch your favorite movie as I try to point out the bad physics}
Josh Langowitz
\\
Starting Bid: \$2
\newline
Eveybody likes to watch movies and laugh bout how they are bad at gettin  physics right. We will watch the movi of your choice and I ill comment on l the bad physics moments as they happen. I recommend Bac to the Future, because the physics is horrible.
\subsection{Improve your all nighter}
Shane Skikne and Chani Martin
\\
Starting Bid: \$3
\newline
Dynamics exam? Transporter due? Chani and Shane will come and make your all nighter bearable! You let us know when, and we'll bring you snacks, coffee, mandatory momentary fun times and moral support throughout the night. We've pulled an all-nighter or two in our day so we'll be sure to throw in a few tips and tricks we've picked up along the way. Must be used this semester.
\subsection{Bouncy Ball Office Hours}
Kristyn
\\
Starting Bid: \$5.00
\newline
You and your friends can bounce as many bouncy balls as you want in my room for 30 min. I will provide the bouncy balls and make sure nothing breakable will be exposed.
\subsection{Play Chutes with Us}
2NW
\\
Starting Bid: \$5
\newline
You know what it is

Come play a lovely game of chutes with the Jubilant Jaime, the Delightful Deborah, the Evangelical Erika, and the Bodacious Brian

For you and a friend... or however many we can tolerate
\subsection{Cameo in our Teaser Concert!}
PowerChords
\\
Starting Bid: \$5
\newline
Every spring semester, PowerChords puts on a themed teaser concert for all of you lovely people!
\subsection{Slumber Party with the R2's}
R2 Team
\\
Starting Bid: \$5
\newline
Wink wink (jk) You choose the R2 room.
\subsection{Night of Poetry in Cambridge}
Sam Chin and Shane Skikne
\\
Starting Bid: \$5
\newline
Sam and Shane will take you and a friend for an awesome night of poetry at the Cantab Lounge in Cambridge or the House Slam in Boston. These are the 2 premier venues in the area. Admission is on us. If bidding goes above \$20, we'll buy you dinner as well.
\subsection{Parcel B Tour}
Paul Titchener
\\
Starting Bid: \$5
\newline
Ever wanted to know all of the secret things in Parcel B? Find anything from the cars to a bag of elephant bones! More money equals more places.
\subsection{Custom Movie/Video Game Night}
Manik
\\
Starting Bid: \$7.5
\newline
You get to pick the movie/video game for a friday night (we'll figure out when) and you get to have it with all your frands in my lofted room (projector and surround sound included). Hopefully schennigans will be involved.
\subsection{Go to the opera or theater with me (SF)}
Ilana Walder-Biesanz
\\
Starting Bid: \$10
\newline
Are you in San Francisco? So am I, and I work as a theater and opera critic. This means I get a pair of premium seating tickets to tons of shows. I have a long waiting list of people who have asked to use my +1 ticket, but with this item you can jump to the top of the list! I'll let you know all the upcoming operas and plays I have (or am likely to have) tickets to, and you get first dibs on which one you want to attend with me.
\subsection{Live that Island Life}
Shane Skikne
\\
Starting Bid: \$10
\newline
Have you ever wanted to live on island time? Spend the day sipping margarita's and hanging out by the beach? Then, don't bid on this item. 

If you have however wanted to join me on a tiny, misshapen, memory-filled island in RI, buy this item. I will do all the organizing to get you and 12-14 of your closest friends the island adventure you've always deserved. From campfires and singing to the one rowboat that got all you to the island floating away, it'll be a night to remember (though for some reason you probably won't remember it). (I don't cover costs, just all planning and organizing.) 

Still thinking about that Margarita on a tropical island? If this item goes for over \$150, I will organize a trip to St. Johns in the US Virgin Islands for you, me and however many friends you want. We'll spend our days hiking, finding private beaches and enjoying the Caribbean water. This trip won't be cheap (\$500+ per person), but it is by far cheapest way to spend a week in the Caribbean. For whom it may concern, drinking age is 18 there. (Once again, I won't cover costs, just research, organizing and planning) (I don't need to come if you don't want me to)
\subsection{2 Tix to see me in The Donkey Show}
Brian Liebson
\\
Starting Bid: \$10
\newline
Come see me in The Donkey Show at Oberon in Harvard Sq!

18+

Choice of 2 dates: Dec 12 or 19 (or 2016 sometime undetermined)

Both are Standing Tix (Floor)
\subsection{Dinner in Somerville/Cambridge!}
Jordyn Burger (c/o 2014)
\\
Starting Bid: \$10
\newline
I love food, and I love conversation. Win this and I'll take you to dinner somewhere nice-ish in Cambridge/Somerville! We'll eat yummy things and chat about life!
\subsection{An Unquestionably Ontological, Questionably Epistemological, Indescribably Illuminating Conversation}
Nur Shlapobersky, Scott Mackinlay
\\
Starting Bid: \$10
\newline
Come sit down with Nur and Scott and move your mouths in patterns which society has deemed meaningful. The higher the bid, the more meaningful and life-changing this conversation will be.
\subsection{Get Your Knight Moves On}
Ryan Louie, Emily Wang
\\
Starting Bid: \$10
\newline
Emily and Ryan will take you on an outing to Knight Moves, their favorite board game cafe! Get ready for games; so many games. 

You may bring up to two additional friends to join in on this quest.

Must be claimed by the end of Fall 2015, since Ryan plans to study abroad next semester!
\subsection{Tour of Pier 9 + Instructables swag bag}
Celeste Maisel
\\
Starting Bid: \$20
\newline
I work at Pier 9 in San Francisco, an office that Business Insider listed as one of the 9 most amazing office spaces on the planet!  I'll take you and a friend on a tour of our multi-million dollar workshop which includes a full metal shop, wood shop, a water jet cutter the size of a flatbed truck, 3D printers and laser cutters, and a view of the bay bridge that can't be beat!  I'll also give you both an Instructables swag bag including t-shirts, mugs, stickers, and a 1 year pro membership to the Instructables website.

If bidding goes above \$40 I'll take you both out to lunch at my favorite lunch place nearby, or you can bring two more friends on your tour!
\subsection{Be part of EH4NN Suite for a Weekend}
EH4NN Suite
\\
Starting Bid: \$20
\newline
Come be a part the lovely suite that includes Alex, Amanda, Claire, Mac-I, Allison, and Eric for a weekend! We'll get you involved in all of our silly suite activities, including, but not limited to, helping Amanda get rid of all the food her mom gives her, fighting with Claire for the beanbag chair, reading instruction manuals with Mac-I, contemplate the intricacies of the english language and couches with Allison, cringing at Eric's rampant shirtlessness, or singing Pentatonix in the shower with Alex (can be separate showers, or you don't have to be in the shower while he is). Other activities include Suite Movie Night, late night pizza, lots of music, and generally being an terrible person.
\subsection{Choose the ACRONYM theme!}
the ACRONYM
\\
Starting Bid: \$25
\newline
Just let us know a week ahead of time, and the ACRONYM will be theme of your choice for one opening. It could be themed around anything (within reason): an unsuspecting friend, FWOlin himself, dogs, and so much more!
\section{Food}
\subsection{One Pint of Home Made Malaysian Peanut Sauce}
Siddhartan Govindasamy
\\
Starting Bid: \$0.1
\newline
Spicy, sweet and vegan. Great with cucumbers, pineapple, jicama, tofu.

Top 3 bids win.

** Contains peanuts
\subsection{Chocolate chip cookies on demand}
Sophie
\\
Starting Bid: \$1
\newline
Good for 1 batch of ~24/36 cookies on demand.
\subsection{Last Bad Day Cookies in your honor}
Shane Skikne
\\
Starting Bid: \$1
\newline
Come December, my time at Olin and Bad Day Cookies (from me, at least) will come to an end. Win this item and the last Bad Day Cookies will be in your honor. Not only that, but I'll bring you like 10 cookies.
\subsection{Truffles!}
Rachel Boy
\\
Starting Bid: \$1
\newline
Alright, friends: it's truffle time! Check out the table below to see how many truffles your donation will get you. I'll work with you to choose flavors for your truffles, and I'll try any flavor you want, no matter how weird or how boring - though if you ask for truffles that are particularly difficult or time-consuming, I may request to make fewer for you. Since I'm in Seattle, getting them to you could get a little hairy, but we're engineers - we'll make it work!

Illustrative Rate Table:
base   up to 20 truffles and 1 flavor
\$20+   up to 30 truffles and 1 flavors
\$30+   up to 40 truffles and 2 flavors
\$40+   up to 50 truffles and 2 flavors
\$50+   up to 60 truffles and 3 flavors
... and so on!

Testimonials:
"These truffles are so delicious I'm never eating anything else ever again, also will you marry me" 
- Everyone who's ever had my truffles

"OM NOM NOM NOM NOM"
- Satisfied customer
\subsection{100 Chocolate Truffles}
Logan Sweet
\\
Starting Bid: \$1
\newline
I will make you 100 chocolate truffles. You can share them with your friends, or you can eat them all yourself. No judgement. (VEGAN AVAILABLE ON REQUEST)
\subsection{Home-cooked Feast for Five}
Victoria Preston and Bill Warner
\\
Starting Bid: \$1
\newline
Bill and Victoria absolutely love cooking, especially for others. They invite you, and up to 4 folks of your choosing, to revel with them over a homecooked* feast prepared by none other than Bill and Victoria. For references on their cooking prowess, email them for names of well-fed customers. Previous feasts have included a full on Thanksgiving Meal and an Autumnal Vegetable Roast. 

*they will actually transport you to a home (Bill's) for the feast. 

- If bidding reaches up to \$40 then you may choose the theme of the feast.
- If bidding reaches up to \$60 you can choose the theme and they will also decorate accordingly.
- If bidding reaches up to \$80 you may choose the theme, there will be splendid decorations, and everyone may wear a silly hat at the table
\subsection{Hippie Food (Granola)}
Becca Getto
\\
Starting Bid: \$1
\newline
noun North American

A kind of breakfast cereal consisting typically of rolled oats, brown sugar or honey, dried fruit, and nuts.

(derogatory)
Denoting those with liberal or environmentalist political views, typified as eating health foods

Whichever definition you prefer is fine! Either way, I will send you a batch of homemade, delicious, nutritious, environmentally conscious, liberal, hippie cereal! Do you like your oats rolled or steel-cut? Does a touch of buckwheat or quinoa tickle your fancy? How about some hemp, flax, or chia seeds to add some extra super-food power! Do you like almonds, pecans, or walnuts? Pumpkin seeds, coconut flakes, or dried fruit? You pick the base, the sweetener, and endless mix-ins! If you're not feeling creative I will don my flower crown, call upon my guiding granola spirits, harness all of my hippie magic and come up with a psychedelic new flavor combination for you! Peace. Love. Granola. \textless 3
\subsection{Bread}
Matt Ruehle
\\
Starting Bid: \$1
\newline
Load. Due to time, yeast, etc, please allow 16 hrs in advance.
\subsection{Cookies and dinosaurs}
Becca Schutzengel and Hannah Sarver
\\
Starting Bid: \$1.93
\newline
We're two alumni from the class of 2013 and we really like baking. Tell us your favorite kind of cookies and we'll make them and mail you (at least) a dozen, to anywhere in the US. And we'll include picture(s) of dinosaur(s), because who doesn't like dinosaurs?
\subsection{Bring you tea!}
Amanda Sutherland
\\
Starting Bid: \$2
\newline
I have lots of tea. It's not terribly classy tea, but I will deliver it to you in a mug. Give me reasonable warning, and I will rush to your location with happiness. Excellent remedy for stress, sickness, and the need of feeling comfy without leaving your chair. No specific limit on times you can cash this in.
\subsection{Three Cakes}
Cecelia Auerswald
\\
Starting Bid: \$2.1
\newline
I'll make three of my favorite cake recipes for you over the course of the year.
\subsection{Cannoli}
Jaime Grau
\\
Starting Bid: \$2.50
\newline
I will take you in a trip to Boston for a Cannoli! or Two!
\subsection{Breakfast in Bed!}
Amanda Sutherland
\\
Starting Bid: \$2.5
\newline
I always have way too much food, particularly breakfast food. I also like delivering happiness. Let me know the night before and I will make you breakfast and bring it to you in bed/your room/your meeting in the dorms. Common things I have are granola, various tasty breads, peanut butter, cereals, hard boiled eggs, tea, hot chocolate, fruit of some variety... you get the idea. Up to three breakfasts available.
\subsection{Trip to Taco Bell}
Ankeet, Saarth
\\
Starting Bid: \$4
\newline
We will take you to taco bell with us!
\subsection{Midnight Anatomically Correct Pancakes}
Annabel, Cecelia, and Keenan
\\
Starting Bid: \$4
\newline
Exactly what it sounds like ;)
\subsection{Breakfast/Lunch/Dinner with Good Company}
Philip Z Loh
\\
Starting Bid: \$5
\newline
I'll be back in Boston for the MIT Mystery Hunt over MLK Jr Weekend. Want semi-interesting, non-dining hall food? I promise to be interesting. Do you?

(I'm buying the meal if that wasn't clear)
\subsection{Homemade lefse!}
Berit Johnson
\\
Starting Bid: \$5
\newline
This is a tasty traditional Norwegian flatbread made from potatoes! Think a cross between tortillas and crepes but made of potatoes. Eat it with butter and cinnamon-sugar! Eat it with lingonberries! Eat it with Swedish meatballs! Eat it with your face!
\subsection{Hot/Cold Brewed Tea}
Brandon Chiou
\\
Starting Bid: \$5
\newline
I have a variety of teas, including Taiwanese high mountain oolong, first flush darjeeling, fruity black blends, greens, and more.

\$5 gets you a pot or 32 oz jar of hot/cold brewed tea. Each \$5 after that gets you another pot or jar.
\subsection{West African honey}
Caroline Condon ('13)
\\
Starting Bid: \$5
\newline
A jam-jar (~250 ml) of honey, mailed to you somewhere in the US (expected delivery: late december). West African honey is darker in color and stronger in flavor (kind of molasses-ey) than North American honey. Also delicious.
\subsection{I'll split a bottle of wine with you}
Nicole Rifkin
\\
Starting Bid: \$5
\newline
I lived in Chile and know lots* about wine. Fanciness of the bottle is proportional to the donation. I'm an adorable drunk. 

*Mostly that its delicious
\subsection{Coffee tour of NYC}
Geoff Pleiss
\\
Starting Bid: \$5
\newline
You like coffee. I like coffee. New York has an amazing coffee scene. Next time you're in the the city let's get crazy caffeinated. I'll take you to the top spots in Manhattan and Brooklyn. And maybe Queens. I'll teach you how to be snobby about these places as well.
\subsection{Cake!!}
Cassie
\\
Starting Bid: \$6
\newline
Tell me what kind of cake you want, and I'll make \& decorate it for you! :)
\subsection{Jar of Lemon Curd}
Zoe
\\
Starting Bid: \$8
\newline
My lemon tree has way too many lemons on it and they keep getting stolen. So I will make you a jar of lemon curd from homegrown meyer lemons.
\subsection{Dinner \& PM Chat}
Ellen Chisa
\\
Starting Bid: \$10
\newline
You \& up to three friends can come to dinner at my apartment in Cambridge. I'll make whatever you want (or whatever I want if you don't give me instructions).

I'll also provide whatever conversation you'd like to have. We can chat about Product Management, life post-Olin, whatever.
\subsection{Asian-Certified Care Package of Instant Ramen Noodles}
Philip Z Loh
\\
Starting Bid: \$10
\newline
I've explored a lot of the available instant ramen noodle brands and have a subjective list of the best. Hint: Does not include Maruchan. If you win, I'll mail you a sizable box of an assortment of noodles. Scales with winning bid amount.
\subsection{Cuban desserts}
Sophia Utset-Ward
\\
Starting Bid: \$10
\newline
I will make you your choice of flan, arroz con leche, merengues,  or capuchinos cubanos (they are mini cakes, not coffee.)

If the bid goes to \$20 I will make 2. 

If someone want all 4 + bonus merengues, the bid will have to go to \$50
\subsection{Mystery Pickles and Jams}
Pickles and Jams CoCurricular
\\
Starting Bid: \$10
\newline
Bid on our item and you'll receive a mystery pickle and a jam from the list below!  Top four bidders will get a pickle and jam and the very top bidder gets double the mystery (2 pickles and 2 jams)!

pickle types:
- mango
- cucumber
- pineapple
- carrot

jam types:
- raspberry, lavender, and mint
- chili pepper
- mixed berry
- blueberry
\subsection{Nachos at Sunset}
Doyung, Saarth, Adam, Adit
\\
Starting Bid: \$10
\newline
We will buy you all the nachos you can eat. 

"Best Nachos in all of Boston" - AJ
\subsection{I will make you Korean Food}
Doyung Lee
\\
Starting Bid: \$10
\newline
Yum. I don't recommend this for vegetarians, as I know mostly meat-based cuisine.
\subsection{I will make you Indian Food}
Saarth Mehrotra
\\
Starting Bid: \$10
\newline
Also yum. I recommend this for vegetarians, as I know mostly vegetarian cuisine.
\subsection{Bonnie's Brownies}
Bonnie (Charles) Tesch
\\
Starting Bid: \$10
\newline
I have been making brownies for about 20 years. I have been donating brownies to the SERV auction for about 10 years. I have gotten pretty darned good at making brownies. I will make you a batch of brownies, customized to your tastes (caramel turtle? s'mores? death by raspberry chocolate? lacking in allergens or ingredients to which you are sensitive? full of magic and baby kisses?), and mail them to you (or someone else) at a time of your choosing.
\subsection{My Best Cupcakes}
Ari Chae ('15)
\\
Starting Bid: \$10
\newline
I mastered a new cupcake flavor this summer - graham cracker bottom, chocolate cake with blackberry filling, and cream cheese frosting. It's the best cupcake I've ever made - the last time I mastered a flavor this good was during my first year at Olin.

Want a dozen shipped to you? You got it. Bid away. :)
\subsection{A Box of Lemons}
Celeste Maisel
\\
Starting Bid: \$10
\newline
I will send you a large, flat rate shipping box of lemons fresh from my parents California back yard, to anywhere in the continental US.  These are not small dainty meyer lemons, but huge, juicy lemons from a decades old, well established lemon tree, seriously, you have never seen lemons like this before.  These lemons will make tons of lemonade, lemon bars, lemon meringue pie...you get the idea.
\subsection{Banana Chip Bread}
Harold Jaffe
\\
Starting Bid: \$10
\newline
I will bake for you a loaf of delicious banana chocolate chip bread and mail it to wherever you are!
\subsection{Malian Tea Set}
Caroline Condon ('13)
\\
Starting Bid: \$10
\newline
I've been living in Bamako for about 5 months, and tea is a big part of my life here - it's what you do whenever you're waiting, welcoming someone, or just sitting around talking. 

I'll send you a teapot, glasses, tea, spices and instructions - everything you need to make Malian style tea. Malian tea is a little like Moroccan tea, except stronger (both more bitter and more sweet).

(I'll mail this when I get back to the US, Dec. 18)
\subsection{BITC}
Annabel, Cecelia, \& Aditi
\\
Starting Bid: \$10
\newline
Brunch in the city!  We will take you to an amazing, hipster location somewhere in Cambridge/Boston and get you an excellent brunch.
\subsection{LNFITC}
Annabel, Cecelia, and Aditi
\\
Starting Bid: \$10
\newline
Late night food in the city - we will treat you to food that is only available after 11 PM.  (Probably better if you're not vegetarian, but we can work something out.)
\subsection{South African Beef Jerky (Biltong)}
Shane Skikne
\\
Starting Bid: \$15
\newline
Win this item and I will make you a lot of South African beef Jerky (otherwise known as Biltong) with my family's recipe and the Biltong machine my grandfather built when I moved to the US. American Beef Jerky is decent, I guess, but a little sweet and kinda gross. Biltong is a bit thicker of meat cuts and usually a little moister with a whole bunch more flavor*. When given to Americans, one described it as "like cool bacon". So yeah. I can't promise you'll like it, but it is definitely my favorite food. If, by some catastrophe, you do regret this item, I will work with you to find a Biltong recipe you do like and remake it to your taste. 

I will start with 2 pounds of beef, but it'll be dried so it'll be less. 
If bidding goes over \$70, I will double the amount of biltong or make it twice. 
I will need to make this when I am home for at least a week so it might take a few months to get it to you. I will either deliver or ship depending on what makes more sense. If you're in the area, you're welcome to come make it with me.  *One other important difference: Biltong is dried over a week, while Jerky is sometimes cooked at low heat. So, you're getting cured, raw, dried meat. I will not get it to you unless it is safe, but I wanted you to know that.
\subsection{Malasadas (Portugese donuts)}
Kelli Shimazu, Lilia Chan, Shruti iyer
\\
Starting Bid: \$15
\newline
Masaladas are delicious doughnuts rolled in granulated sugar! The top bidder will get any amount of piping hot fresh doughnuts (up to 3 dozen).
\subsection{indibobo come-back for a day}
Ambika
\\
Starting Bid: \$20
\newline
I will host indibobo one more time in my suite with indian food and boba! Get to \$40 and the highest bidder gets to choose the menu.
\subsection{Superlative Dining Experience for Two}
Isaac Vandor
\\
Starting Bid: \$20
\newline
Tired of dining hall food? Want to treat your significant other to a nice meal without leaving the building? I will work with you to develop a menu of your choice for a three course meal (appetizer, entree, dessert) to treat you and one other lucky person to an extraordinarily awesome dining experience. (Bonus points if the meal is entirely vegan)
\subsection{A Lovely Cake }
Claire Beery
\\
Starting Bid: \$20
\newline
I will make you a cake during spring term. It will be lovely and delicious. Higher bids = more complex design. Design is my prerogative but you can pick the theme.  Starting bid gets you a 2-layer 6" round cake or equivalent. Date and theme must be decided by 1st of January.
\subsection{Homebrew Adventure}
William Saulnier
\\
Starting Bid: \$20
\newline
I have always been interested in Homebrewing. And I want to give it a try! On this Homebrewing adventure, you will help me select what my first ever homebrew will be! I'll buy all the gear, I'll buy all the supplies, and you can help (or not) me with the brewing. And, of course, you'll have first tasting rights when it's ready, and I'll update you on it's status as much (or as little) as you want. Warning; I'm completely new to this, the results may not be drinkable, and did I mention I'm completely new to this?

If we raise at least 40 dollars, I'll let you chose the second batch too! Which is bound to be better than the first, right?

You, of course, must be 21 or older to drink anything I give you.
\subsection{NINJA your class at IHOP}
Josh Langowitz
\\
Starting Bid: \$25
\newline
I will take you to IHOP, buy you food, and NINJA the class of your choice for you (note that for most classes that aren't ECE or E:C or Math I will be about as useful as Google). Additional people are \$15 per person and you need to provide transportation after the 4th person, not including me.
\subsection{Wok Cooking Lessons at Mel's House}
Mel Chua
\\
Starting Bid: \$40
\newline
Mel recently inherited her family's wok (originally her parents' wedding present; it is older than she is). She's learning how to use it. She can teach you, too.

This item is for up to 4 bidders to come to Mel's house for dinner on some mutually agreeable evening. We will choose recipes from a stir-fry cookbook in advance; Mel will get ingredients, and we will cook a glorious Chinese dinner, with Mel instructing the group in wok technique.  Then we will eat it. It will be delicious. (If not, Mel will hurriedly call in delivery from the Chinese restaurant down the street. But so far, the results have been deliciously edible.)

Special dietary needs will be accommodated. Transit to/from Olin is available if needed. (Bonus: Mel's house is also Eric Van Wyk '07's house, though she cannot guarantee his presence.)
\subsection{Vermonster Adventure}
Josh Langowitz
\\
Starting Bid: \$40
\newline
I will take you (or you and a group of friends, up to 5 including me or else you need to provide the extra transportation). Top 2 bids both get Vermonsters, but they need to happen at least a week apart. 2 person Vermonsters not recommended, but I'll try if you are really that committed. 3 people is hard, but I've done it by not eating anything else that day. I'd recommend 4-5 hungry, high-capacity people or 6-8 people interested in a lighter meal or desert.
\subsection{NEEDHAM PIZZA TOUR 2K15}
Mitch Cieminski
\\
Starting Bid: \$50
\newline
Do you like science? Do you like pizza? I have a pizza-related question that can only be answered by science. WHAT IS THE BEST PIZZA IN THE TOWN OF NEEDHAM?

I've identified all 13 subjects for the experiment.

Sweet Tomatoes
Kostas Pizza and Seafood
Domino's Pizza
Needham House of Pizza
Hearth Pizzeria
Comella's
Not Your Average Joe's
Cowlick's Deli
Nicholas' Pizzeria
Bertucci's
Town House of Pizza
Gianni's Pizza and Deli
Brothers Pizza and Restaurant

Experimental Method:
We go to Needham on a Saturday
We go to every restaurant on the list of subjects
At each restaurant, we split one (1) small pizza, half cheese, half "house choice"
I WILL PURCHASE ALL PIZZAS
We compare cheese as a baseline
We compare "house choice" as a measure of each eatery's understanding of pizza as a comestible medium

Expected results:
We will be very full
We will know the best pizza in the town of Needham
Need there be anything else?

Experimenters can either be just you and me, or we can take along some friends if you'd rather do that. Split it however you want. I'm also willing to divide the experiment among multiple days (no more than 3 total days).
\section{Lessons}
\subsection{Teach you to make omlets}
Adam Coppola
\\
Starting Bid: \$0
\newline
I'll tell you my secret family recipe and we'll make breakfast.
\subsection{Become a Pokemon Master}
Mitch and Alex
\\
Starting Bid: \$0.01
\newline
We will teach you how to become a Pokemon Master. You will be the very best, that no one ever was. To catch them is your test, to train them is your cause.
\subsection{Scrapbook Advice/Lessons}
Jessica Diller
\\
Starting Bid: \$0.50
\newline
I made a 150 page scrapbook over the summer to organize all the pictures and bits from my 5-week europe trip. I learned a lot, like where the cheapest photo printing is in large quantities, which glues go the furthest, and how to shop the deals at Michael's. Let me be your scrapbook mentor!
\subsection{Gym Chat}
Brian Liebson
\\
Starting Bid: \$1
\newline
Brian will talk to you about gym things and working out. You'll get all ripped and stuff broh
\subsection{Guitar Hero Lesson}
Haley Pelletier
\\
Starting Bid: \$1
\newline
Are you dissatisfied with your Guitar Hero skills?  Do you want to be able melt faces with a small, plastic guitar, but don't have the time and/or patience to practice?  In one 30-minute session, I will impart years of wisdom to you.  You'll probably get at least a little bit better.  But I make no promises.

Game \& equipment supplied by me.
\subsection{Flow Wand Lessons}
Alex and Claire
\\
Starting Bid: \$1
\newline
You know that magical flowy levitating thing that we always amaze you with during OFAC burns? Become our apprentice. We will teach you our ways. You will learn the true power of the Force.
\subsection{No Filter with Grace and Shane}
Grace and Shane
\\
Starting Bid: \$1
\newline
Have you ever wondered what people thought of you? (Specifically Grace and Shane)  You have the opportunity to get 10 minutes of unfiltered feedback on how the dynamic duo see you. \#constructivefeedback \#nonconstructivefeedback \#it'sok2cry \#thisisalearningexperience4allofus \#hashtag
\subsection{Programming Lessons}
Brandon Chiou
\\
Starting Bid: \$1
\newline
A fan favorite for three years! I'll teach you everything I know on the following languages: Python, C, C++, COBOL, BASIC, FORTRAN, Perl, Ruby, ROR, English, Spanish, and Chinese.

If you're not satisfied, I'll take you out to get some delicious ramen. And pay for it. No, it won't just be the two of us.
\subsection{Coding interview prep}
Dennis Chen
\\
Starting Bid: \$1
\newline
Three one hour coding interview prep sessions. I'll let you borrow resources, give you general advice, and do mock interviews with you so you can ace your next technical interview!
\subsection{Riven Tutorial}
Jack,  Tran
\\
Starting Bid: \$1
\newline
Champion match-up, Team comp analysis, Animation cancelling, Bugs \& tricks, Itemization, Road to Challenger
\subsection{Bad Cad}
Grace and Chani
\\
Starting Bid: \$1
\newline
We'll critique your CAD. We'll give you tips on good CAD modeling practices.
\subsection{Book List}
Bonnie (Charles) Tesch
\\
Starting Bid: \$2
\newline
Want to learn about a new subject? Looking to branch out of your genre? Just finished a series and not sure what to do next? I work in a public library, and I really like helping people find things they want to read. I'll chat with you about your desires and your interests, and curate a suggested reading list of at least 10 books you have never read before that I think you'd like. All suggestions will be available on Amazon and/or your local public or academic library system.
\subsection{Knot Savvy}
Rebecca Jordan
\\
Starting Bid: \$2
\newline
I teach you knots! If you want to learn to make a pulley system out of a single rope, can't remember how that "bunny goes around the tree" mnemonic goes, or just want to attach a bunch of ropes together, I can help. I'll work with you on whatever knots you want to learn, whatever your skill level. (If you know more than me we'll go on a quest of discovery together.)
\subsection{Beard/General Facial Hair Care Advice}
Manik and Joe Sutker
\\
Starting Bid: \$4
\newline
Joe and I will give you advice on how to properly grow and care for your facial hair. As experts in the field, this will likely be full of shenanigans. All encouraged to bid on this **Beards not required for getting this item. 

***compulsory pun: I didn't like my beard at first. But now it's growing on me.
\subsection{Knife Throwing Lessons}
Brandon Chiou
\\
Starting Bid: \$5
\newline
Modsim taught me how to throw knives*. I have throwing knives. Let's go throw knives. 

*wat
\subsection{Dutch Lesson}
Stijn Vandycke
\\
Starting Bid: \$5
\newline
Are you interested in learning Dutch? 
I will teach you some important phrases and words that you should know as well as any phrases you request.
\subsection{Learn something with you}
Shane and Nicole Rifkin
\\
Starting Bid: \$5
\newline
Have you ever wanted to learn anything? Us neither. But just in case something ever comes that you do want to learn, we will learn it with you! You name the thing, we'll find a way to learn it with you! Knitting? Race car driving? The math? If it costs money, you'd pay for your lesson and we'd each pay up to half of what you bid on this for our lesson. 

If need be, we can make sure we're worse at it than you are!
Nicole wants to add that you learning things is the literal cutest.
\subsection{Rope Dart Lesson}
Paul Titchener
\\
Starting Bid: \$5
\newline
Lessons on the fire arts prop rope dart
\subsection{A Rope Dart Lesson With a Twist}
Mackenzie Frackleton
\\
Starting Bid: \$5
\newline
Learn rope dart from Paul with me! He's contractually obligated to give me a lesson from last year's SERV auction and I have not cashed in on it yet. We pick when/where and what we learn.
\subsection{Knife throwing Lesson}
Paul Titchener
\\
Starting Bid: \$5
\newline
Learn how to throw knives
\subsection{Crash-Course in Harp Playing}
Julia O'Donnell
\\
Starting Bid: \$10
\newline
In 45 minutes I'll teach you how to play a simple tune on the concert harp!
\subsection{Crochet lessons }
Stijn Vandycke
\\
Starting Bid: \$10
\newline
Have you ever wanted to learn to crochet? I will teach you.
Lessons:
\$10- Learn to make a Belgian flag
\$20- Learn to make a scarf
\$30- Learn to make a hat
\$35+- Learn to make a plush animal
\subsection{Sewing lesson}
Sophia Utset-Ward
\\
Starting Bid: \$10
\newline
Have you ever wanted to make your own clothes? I can teach you some basic stuff on how to make them.
\subsection{[removed]}
[removed]
\\
Starting Bid: \$10
\newline
[removed]
\subsection{making balloon animals}
Sophia Utset-Ward
\\
Starting Bid: \$10
\newline
making balloon animals like dogs, turtles, etc. Or you can be original and go for your own design.The sky is the limit.
\subsection{Sailing!}
Amanda Sutherland
\\
Starting Bid: \$10
\newline
I will teach you about sailing (if you need it), and I will take you sailing! Not sure exactly where, but it will happen. This item is best if you have a friend join you :)
\subsection{Photo Adventures}
Brandon Chiou, Forrest Bourke
\\
Starting Bid: \$10
\newline
Wanna shoot street style like The Sartorialist? Take your money somewhere else. Feel like you can improve your landscape game but you don't know how? Take your money somewhere else. Wanna learn how to do some epic studio lighting? Well,....also take your money somewhere else.

Depending on what you want to shoot, we'll accompany you and provide "insightful critique" and "constructive" criticism. You'll be more than satisfied with what you get. Transportation provided. Read our testimonials below!


"Brandon and Forrest helped me on my selfie game" - Ansel A.

"I learned everything I knew about studio lighting from this dynamic duo" - Annie L.






PS: Follow us on Humans of Needham.
\subsection{The Boston Climbing Experience}
Ryan Louie, Emily Wang
\\
Starting Bid: \$10
\newline
Ryan and Emily will give you a bouldering lesson at Rock Spot South Boston, and treat you to food at Chinatown afterwards! You may bring one additional friend to join in if desired.

Must be claimed by the end of Fall 2015, since Ryan plans to study abroad next semester!
\subsection{Dutch Knowledge and Belgian Beer}
Wannes Vanheusden \& Jannes Van Noyen
\\
Starting Bid: \$15
\newline
Learning Dutch and drinking Belgian beer, all you need to know to survive in Belgium! \textless 3
\subsection{1 hour dance lesson}
Zach Brass
\\
Starting Bid: \$20
\newline
I've been a local lindy hop and blues dance teacher around the Boston area for a few years now and have just started booking teaching gigs throughout the northeast. I've danced for weddings and galas. I've danced at the New England Conservatory. I've even been part of the opening act for Postmodern Jukebox. It's safe to say I know my stuff. And now you can know my stuff too! If the price goes high enough, I'll make the lesson even longer.

No limit on how many people are in this lesson. This can be a 1 or 2 person private lesson or a group lesson.
\subsection{Mountain Climbing Adventure and Lesson}
Jaime McCandless and Jason Curtis
\\
Starting Bid: \$50
\newline
Jason and I have gone on many climbing adventures in the snow-covered mountains outside Seattle. Join us on a one-day expedition to one of the mountains in the Seattle area and we’ll teach you how to kick steps in snow, navigate through forested and foggy terrain, ice-ax arrest, plunge-step, and glissade. 

We’ll bring technical equipment (ice-ax, etc), you bring appropriate clothing for snow travel. No experience necessary! Reasonable physical fitness encouraged.

If the bidding gets over \$100, you can either bring a friend or we’ll convince Andrew Fabian to come along (and he’ll kick all the steps).

If the bidding gets over \$200, we’ll make it an overnight trip and teach you how to build a snow cave or igloo (your choice).
\section{Services}
\subsection{What is in my microwave?}
Sophia Seitz
\\
Starting Bid: \$0
\newline
Do you always forget things in the microwave? If you buy this item, I will tell you what is in the microwave closest to me for a time depending on the winning bid. I can also send these emails to someone else, provided they're okay with this. For every \$2 that is donated, I'll tell you what is in my microwave for a week!
\subsection{Dungeon master on demand}
Tom chen
\\
Starting Bid: \$0
\newline
I will run/play/teach a game for you. By default this will be Dungeons and Dragons fifth edition but I can do anything you supply materials for.
\subsection{Pokemon Breeding}
Mitch and Alex
\\
Starting Bid: \$0.01
\newline
The two expert Pokemon Breeders of the Franklin W. Olin Pokemon League are offering their services as Master Trainers. We will train pokemon for you (Gen 6 only), and make them the best/most fun they can possibly be, according to the following rules:
 
\textless \$2.50: We will breed and train a pokemon for you with a skillset that we think is just hilarious.
\$2.50-\$5: We will breed and train a battle-ready pokemon for you that can be used competitively.
\textgreater \$5: We will breed and train a battle-ready pokemon of your choice.

After every multiple of \$5, we will add on another pokemon. No more than 25 percent of the total pokemon will be just hilarious. The remainder will be great. We promise.
\subsection{Magical Adventure with Greg and Dennis}
Greg Coleman and Dennis Chen
\\
Starting Bid: \$0.01
\newline
We will take you and up to four friends on a magical adventure.
\subsection{A Hug}
Lydia Z.
\\
Starting Bid: \$0.05
\newline
A warm hug, to be delivered to you on the day of your choice.*

*Not valid during vacations or after 2019.
\subsection{Parent Your Burgeoning Relationship}
Austin and Ellie
\\
Starting Bid: \$0.5
\newline
Miss having your parents around to helicopter inches above your courtship with New Sweet Thang? You're in luck! Austin and I will help you pick out what to wear, make pointed comments about Are You Sure You Want To Wear Your Hair That Way, recommend favorite date spots in and around Boston, drive you two on dates, and watch you eat dinner through the restaurant window. Kidding on that last one! Maybe. And if disaster should strike, we'll make you hot cocoa and remind you that You're Way Out Of That Loser's League, Anyway.
\subsection{Makeover}
Inseong
\\
Starting Bid: \$1
\newline
Get a makeover for a special occasion any time you want! (If you can trust me)
\subsection{Bedtime Storytime}
Liani, Lindsey, Ian, \& Nick
\\
Starting Bid: \$1
\newline
We will conduct a dramatic reading of a story of your choice.

\$2 - One of us will tuck you in
\$5 - You can choose which of us will tuck you in
\$10 - All of us will tuck you in
\$25 - We will provide tea and your choice of chocolate or cookies

You may bid as a group.  We may or may not tuck in all of you.
\subsection{Help You Select a Bow Tie}
Alexander Crease
\\
Starting Bid: \$1
\newline
Always liked bow ties but never found one that fits your style? I'll go through my massive database of bow tie vendors and help you pick one! I will also teach you how to tie it!
\subsection{Teach You How to Tie a Bow Tie}
Alexander Crease
\\
Starting Bid: \$1
\newline
I'll teach you how to tie a bow tie! Soon, you'll know it so well you'll be able to do it with no mirror.
\subsection{Sound Effects of Your Life}
Alex and Myles
\\
Starting Bid: \$1
\newline
We will follow you around and make the sound effects of your life. \$10 for every hour.
\subsection{An Adventure}
Shane Skikne
\\
Starting Bid: \$1
\newline
I will plan and organize an adventure (to the extent adventures can be organized). I'll come and we'll have the time of our life. If bidding goes above \$100, I'll organize a multi day adventure. If bidding goes above \$300, I'll organize us a trip to somewhere awesome. 
(I don't cover cost for these adventures, I just do all the pre-adventure research, planning and organizing).
\subsection{Be our Third}
Rahil Dedhia and Saarth Mehrotra
\\
Starting Bid: \$1
\newline
With a honey in a middle there's some leeway
\subsection{Fantasy Football Help}
Rahil Dedhia
\\
Starting Bid: \$1
\newline
I will help you manage your fantasy football team
\subsection{Wagon me around}
Ankeet Mutha
\\
Starting Bid: \$1
\newline
You get to wagon me around for a day. Go wherever you want and I'll go. I WILL NOT leave the wagon no matter where you take me.
\subsection{Personal Trainer}
Rahil Dedhia
\\
Starting Bid: \$1
\newline
I will be your personal trainer.
\subsection{Let's Play a Game}
Ankeet Mutha, Dimitar Dimitrov
\\
Starting Bid: \$1
\newline
Dimitar and Ankeet will play some of our favorite games with you!
\subsection{Bad Life Advice}
Rahil Dedhia and Saarth Mehrotra
\\
Starting Bid: \$1
\newline
Sometimes you need people to encourage you to make those bad decisions
\subsection{[removed]}
[removed]
\\
Starting Bid: \$1
\newline
[removed]
\subsection{Water Colors}
Saarth Mehrotra
\\
Starting Bid: \$1
\newline
For every \$5, I will make a shitty water color painting for you! We can come up with ideas together.
\subsection{Eat the Firiest Burrito}
Ankeet Mutha, Saarth Mehrothra, Aidan McLaughlin, Adit Danushkoti
\\
Starting Bid: \$1
\newline
We like spicy food. You might like spicy food. Eat the spiciest burrito ever with us. This burrito literally made some of us cry already.
\subsection{Hour with Saarth}
Ankur Das
\\
Starting Bid: \$1.00
\newline
Saarth's a pretty cool dude, I guess? If you really want to pay money to hang out with Saarth for an hour (and talk about ANYTHING), go for it?
\subsection{Fantasy Football Advice (Better than Rahil)}
Saarth
\\
Starting Bid: \$1
\newline
I am 7-0, Rahil is 2-5.... enough said
\subsection{1 hour with Ankur}
Saarth
\\
Starting Bid: \$1
\newline
He is Dank. Get to know him.
\subsection{Adventure}
Saarth, Doyung
\\
Starting Bid: \$1
\newline
We will plan and execute an excellent adventure.
\subsection{Solve your problem}
Evan Dorsky, Saarth Mehrotra
\\
Starting Bid: \$1
\newline
It's like a wish from a genie. We will do anything in our power to solve one of your problems.
\subsection{Extra Time}
Philip Z Loh
\\
Starting Bid: \$1
\newline
Ever feel like the East Coast is way too fast and you're constantly out of time? Good thing Seattle is 3 hours behind! Win this and you'll get 3 hours of my time to help you with stuff that I can do from here...

P.S: I have nothing in mind and am hoping that I won't regret this... :P
\subsection{Help You Adult}
Philip Z Loh
\\
Starting Bid: \$1
\newline
Adulting is sometimes hard. Want potentially useful help/advice?

P.S: Winnable by students only; no real adults. ;)
\subsection{Phone calls for life on your birthday}
Graham Hooton
\\
Starting Bid: \$1
\newline
It's nice to get phone calls on your birthday! It's nice to keep in touch with friends over the years, even if it's only once a year.

Tell me your birthday, and I'll call you on it every year for the rest of our lives.
\subsection{A Serenade}
PowerChords
\\
Starting Bid: \$1
\newline
The most wonderful, angelic voices you have ever heard will give you or a friend (or an enemy) a beautiful serenade. For up to \$25, we will sing a song from our current repertoire, for over \$25, we will spend a bit of time learning a song of your choice to sing.
\subsection{Puns. Lots of Puns.}
Alexander Crease
\\
Starting Bid: \$1
\newline
I can, and will, make lots of puns. For every dollar donated, I will make 5 minutes of puns based on everything you say, see, or do. For over \$15, you will be able to choose who you wish to be PUNished and I will follow THEM around and make lots of puns.
\subsection{A Mix Tape}
Alexander Crease
\\
Starting Bid: \$1
\newline
I will make a personal mix tape for you based on your personality, and what kind of emotions you want in it!
Under \$10, it will be all digital
If over \$10, I will put it on a CD with some album art
If over \$20, I will put it on a CD and a cassette tape, because who doesn't love cassette tapes?
\subsection{Secret High Five}
Alexander Crease
\\
Starting Bid: \$1
\newline
We'll make our own, super top-secret high five that nobody else will be able to replicate.
\subsection{Otomatone Serenade}
Anne LoVerso
\\
Starting Bid: \$1
\newline
I have an otomatone, which is a beautiful-sounding* musical instrument.  At a time of your choosing, I will serenade you or a person of your choosing with it.  I don't actually know any songs (or notes?) on it, so "serenade" is used loosely here to mean something more along the lines of "make noises at"

*subject to interpretation
\subsection{Help you make Amanda sad}
Eric Schneider
\\
Starting Bid: \$1
\newline
People frequently like making Amanda sad*, for various reasons. If you win this item I will aid and abet your plans to the best of my ability. My involvement will scale with your donation!  *Think pranks or other shenanigans. Also, this has Amanda's consent :)
\subsection{Curated Tinder Profile}
Daniel Leong
\\
Starting Bid: \$1
\newline
I will make your Tinder profile watertight. Perks include judgmental looks and maximized matches. 

Reviews:
"I guess that guy wasn't awful" -Zoe F, Berkeley CA
"Why the @\#\$@ did you swipe on that guy?!" -Deborah H, Greensboro NC
\subsection{Photo Shoot}
Charlie
\\
Starting Bid: \$1
\newline
Get your photo taken by me! Satisfied customers of the past include Hannah Wilk, Austin Greene, and Ellie Funkhouser.
\subsection{Couple's Therapy}
Nicole Rifkin
\\
Starting Bid: \$1
\newline
I will tell you how adorable you and your partner(s) are together and aggressively remind you how beautiful you and your partner(s)'s current/future offspring are/will be. 
You can also bid on this for a friend!
\subsection{Got Ultimate Bed Hair?}
Ryan Louie
\\
Starting Bid: \$1
\newline
Have you ever seen Ryan lurking through campus, with the craziest bed hair you've seen?

"My god, he just looks like he just woke up! And it's like 2pm right now too!"

"Dude, I would not mess with that beast.  I've heard that it sticks up like that for days."

"Does he put, like, gel in it?"

"It's the perfect synergy between unintentional and artful."

"I want to experience this for myself!!!"

Yes, yes, if any of these statements resonates with you, YOU should come and learn about the dark art of getting your bed hair style on, from yours truly.
\subsection{SERV Auction Insurance™}
Mitch Cieminski
\\
Starting Bid: \$1
\newline
There are you are. At the SERV Auction. Bidding on your favorite item. You're so excited to get it! You win your item. You're stoked to redeem it. You email the person who offered it ... and they take FOREVER to get back to you. They're slow on scheduling, they're taking a while to make it, and it generally just seems like it's not going to happen. In some cases, it never does...

Then you remember that you bought SERV Auction Insurance™! You simply contact Mitch Cieminski Insurance Company, tell them that it's been more than 4 months since the SERV Auction and that an item you won is unfulfilled, and they'll provide you fair compensation* for your loss!

*"fair" compensation is defined as things that Mitch can do or attempt to make up for your item. It may or may not be an exact replica of the original item. Depending on the amount of the bid or how awesome he thinks the item is, Mitch may or may not decide to spend money on fulfillment (but an appropriate amount of time is guaranteed).

The top three (3) bidders will be insured and pay SERV their bidding amount.
\subsection{Fake Boyfriend for a Day/Evening}
Brian Liebson
\\
Starting Bid: \$2
\newline
Got a double date? Got no date? I'll be your fake boyfriend for a day/evening. Show me off, I'll walk around shirtless, it'll be hot.

*If I see a hot man I'm going to stop mid-date and we can go on another fake date another time
\subsection{Drink Water with Us}
2NW
\\
Starting Bid: \$2
\newline
We'll drink water together. Credit to Jaime for the idea.
\subsection{Cheese Please}
Kristyn Walker, Hannah  Wilk
\\
Starting Bid: \$2.00
\newline
Hang out with Hannah and Kristyn. Eat cheese and chocolate. Have chill chats.
\subsection{R2 Cents}
R2 Team
\\
Starting Bid: \$2
\newline
Let us know a tough issue you're going through and each one of us will provide you with our personal insight.
\subsection{Recommend you books}
Eric Schneider
\\
Starting Bid: \$2
\newline
I like reading a lot, and also gushing about how great I think certain books are. For every two dollars I'll tell you all about a book I think is great, maybe make a big list with what I like about them. If I have the books, I'll lend them to you.

Most of the books I'll recommend will be fantasy or sci-fi, but there's a fair range inside of that if you have any preferences.

Some favorite authors: Pratchett, Gaiman, Michener, McCaffrey, Pratchett, John Ford, Zahn, and Pratchett
\subsection{Review your grad school apps}
Geoff Pleiss
\\
Starting Bid: \$2
\newline
As someone who had to go through the process last year, I know what you're going through. I'll do a read-over of your personal statement and give you all sorts of other advice.
\subsection{Permission for All-students Email}
Brian Liebson
\\
Starting Bid: \$2
\newline
I will give you permission to write an all students email.
\subsection{Photo Shoot}
Forrest Bourke
\\
Starting Bid: \$2.5
\newline
You have zero artistic freedom.

If the bidding goes above \$50, I'll make a magazine and give you two copies. (Plus the PDF)

If the bidding stays under \$5, Shane gets to do your hair.
\subsection{Do your makeup}
Shrinidhi
\\
Starting Bid: \$3
\newline
I'll do your makeup for an event - artistic, costume, casual, formal, whatever style you wish. You can look at my pf pic on FB for an idea of my favorite kind of dramatic makeup. Of course if you just want to look nice, and not like a scary beautiful raven, I'll do that too.
\subsection{DIY up your clothing}
Shrinidhi
\\
Starting Bid: \$3
\newline
If you don't know, I have a DIY fashion youtube channel (You should check me out @ Cherish Scraps!) I like to turn old boring clothes into new nice clothes with scissors, and possibly a needle and thread. If you have an old clothing item you can't bear to get rid of, but never wear, I'll transform it for you.
\subsection{Bedtime Story with Maire}
Maire Keene
\\
Starting Bid: \$4
\newline
I will read to you for half an hour from any book in my lending library you choose --or your library... or THE library... wherever you want to get your fix.
;)
If the bid goes above 10 dollars, I will read to you for an entire hour!
\subsection{Post-it your life}
Doyung Lee
\\
Starting Bid: \$4
\newline
Need to figure out your life? I can't figure it out for you , but we can ideate/organize/reflect/plan out your life with post-its!
\subsection{Backup Dancing}
Jessica Diller and Brian Liebson
\\
Starting Bid: \$5
\newline
We will backup dance for you for like a song or two. Jessica will definitely not take her shirt off.
\subsection{Haircuts}
Liani
\\
Starting Bid: \$5
\newline
I like giving haircuts.  You need (or will soon need) a haircut.  Let's do this.

Most recently shorn: Meghan Tighe, Myles, Bika, Eric Franzie.
\subsection{Weekly Climbing Psych for One Year}
Erika Swartz '12
\\
Starting Bid: \$5
\newline
If you win this item, I will send you something climbing-related every week!   

Items could include articles on all subjects from my archive of unorganized  internet bookmarks, amazing climbing photos from around the world, climbing magazines, chalk blocks, links to funny, interesting, or inspiring videos, and anything else climbing-related that I dream up in a year of sending you things.
\subsection{Postcard from East Africa}
Erin McCusker
\\
Starting Bid: \$5
\newline
Ever want a snapshot of life in Kenya? For your donation (multiple allowed!) I will send you a postcard from Kenya where I currently live and describe to you they day and any recent notable highlights of the season!
\subsection{1 year Rocksbox membership (worth \$180)}
Rocksbox
\\
Starting Bid: \$5
\newline
Rocksbox is a subscription jewelry rental service. One year of membership will allow you to borrow three pieces of designer jewelry at a time.
\subsection{Buy you coffee and question your life}
David Pudlo
\\
Starting Bid: \$5
\newline
We will go sit down at a coffeeshop and I will question your life.
\subsection{Needham Forrest Surpise}
Kristyn
\\
Starting Bid: \$5.00
\newline
I'll take you to something cool in the Needham forrest. It's a surprise!
\subsection{Drive you around}
Ankeet Mutha
\\
Starting Bid: \$5
\newline
I'll wagon you around wherever you want for a day! You won't have to get out of the wagon.
\subsection{Computer Help}
Tom Chen
\\
Starting Bid: \$5
\newline
I will do magic computer things* and your computer MAY work better. \$5 per hour.

*magic computer things include:
-hunting for malware
-editing startup programs so they don't dogpile your computer at boot
-doing boring things you really should have done like updates and backups
-physically taking the thing apart
-physically putting the thing together
-finding something wrong in between the two above steps
\subsection{Graphic Design Logo}
Keenan Zucker
\\
Starting Bid: \$5
\newline
Need a sweet, vectorized logo of some sort? I like doing minimalist ones, but I'll work with you to create a cool logo of something. I could vectorize your face for a personal website, create a project logo, a laptop sticker design, etc.
\subsection{I will cut your hair}
Claire Diehl
\\
Starting Bid: \$5
\newline
I cut peoples hair sometimes. Want me to cut yours?
\subsection{We will cut your hair}
Claire Diehl and Amanda Sutherland
\\
Starting Bid: \$5
\newline
We cut hair sometimes (individually). We will cut your hair (together). Possibly with one of us cutting each half. Don't worry, we won't make it unpleasant (unless you want it to be).
\subsection{Three Tall White Guys}
Patrick, Scott, \& Keenan
\\
Starting Bid: \$5
\newline
We will take YOU out on a romantic dinner date. That's right, three tall white guys will compete for your affection AND pay for your dinner. The more money, the fancier we will dress (or undress)
\subsection{Dumpster Bagels}
Kristyn
\\
Starting Bid: \$5
\newline
I'll take you and one other person to get dumpster bagels late into the night.
\subsection{Ask me anything}
Maia Bittner
\\
Starting Bid: \$5
\newline
You can ask me anything - I'm particularly good at career advice as long as it's convincing you to start a company, making intros, ranting about feminism, giving advice on how to create a REALLY scrappy website/company, and complaining about cars.

Skype call or in person in San Francisco.
\subsection{Your floor R2 will make your bed for a week }
R2 Team
\\
Starting Bid: \$5
\newline
Hate coming home to a messy bed? Well, with the help of your floor R2 this problem can be solved.  Add a bed for every \$25. Other R2 help may be enlisted  (For one week only)
\subsection{Comfy Rant Time in a Blanket Fort}
Raagini Rameshwar
\\
Starting Bid: \$5
\newline
Do you have things you need to get off your chest? Don't know how to properly express yourself without the comfort of blankets and hot cocoa? Come hang with me in a rad blanket fort complete with pillows and hot drinks, and rant about school, jobs, life, anything! Infinite coziness included.
\subsection{Hulu and Hang with Glory Hall}
Glory Hall
\\
Starting Bid: \$5
\newline
Does anyone even use hulu anymore?
\subsection{Pole dancing lessons from Aidan}
Daniel Leong
\\
Starting Bid: \$5
\newline
Aidan (formerly '16) will teach you how to pole dance. Pole included.
\subsection{PM Interview Help}
Daniel Leong
\\
Starting Bid: \$5
\newline
If you need help or just want to chat about what PMing entails, I'm happy to help.
\subsection{Help you build a computer}
Josh Langowitz
\\
Starting Bid: \$5
\newline
I will help you find and order parts for and then build a personal desktop based on your needs. Probably best if used for a gaming rig because that's what I know.
\subsection{Study abroad advice}
Jamie Gorson
\\
Starting Bid: \$5
\newline
I spent a lot of time planning my study abroad, from developing my own program to exploring everything that is out there. I would give you help and advice for the best ways to go about studying abroad and help you get through the stress of applications to visas.
\subsection{Be your gym buddy}
Jamie Gorson
\\
Starting Bid: \$5
\newline
Need someone to get you out of bed? Want to work out but not think about what you should be doing? Well I'm here to help! Join me for a workout and I'll plan the whole thing! 
Sophia Seitz said this morning: "Jamie you're killing me!" With a smile on her face.
\subsection{Balanced life advice}
Myles and Jamie
\\
Starting Bid: \$5
\newline
 We'll both give conflicting (but convincing) advice on any issues or decisions you're facing
\subsection{Read the names at Super Senior Graduation}
The Class of 2015.5
\\
Starting Bid: \$5
\newline
Have you ever wanted to read a list of names? Now is your chance! You get to read the names at Super Senior Graduation. If this goes above \$15, you can even add your own middle ames.
\subsection{Possible Hypnosis with Definite Meditation}
Shane Skikne
\\
Starting Bid: \$5
\newline
At one point in my life, I knew how to do hypnotism. I haven't done it in 4 years, but I am happy to try again. Win this item and I'll try hypnotise you and friend(s). Note, there is a good chance this will not work, but then you'll end up just getting some nice guided meditation from me (aka I'll talk at you in a soothing voice for 30 minutes to an hour about oceans and relaxation).
Must be used by the end of the semester.
\subsection{Cad you a thing}
Lindsey Andrade
\\
Starting Bid: \$5
\newline
Want something CAD'ed? I will CAD you something! Want a cool loft of something awesome 3d printed? I'm your person. (Will not CAD anything for course work, but can help if you want)
\subsection{Resume and essay editing}
Ilana Walder-Biesanz
\\
Starting Bid: \$10
\newline
Not only was I an Olin writing tutor; I also worked as a college admissions resume and essay editor for six years. I can help you make your grad school application materials (or fellowship application materials---I have extra-much experience with those) as awesome as possible. The volume of essays I'm willing to look at will scale with the size of the winning bid.
\subsection{Boston/Cambridge/Allston Adventure Time}
Doyung Lee
\\
Starting Bid: \$10
\newline
Let's go adventure in Boston/Cambridge/Allston. I know some cool/fun/weird places we can hang out! You and 2 friends.
\subsection{Personalized Tour of Ithaca, NY}
Lorraine Weis (Class of 2011)
\\
Starting Bid: \$10
\newline
Thinking about Cornell as a grad school? Love upstate New York, lakes, or gorges? I will give you a personal tour of Ithaca, Cornell, and the surrounding area, depending on your interests. Could include hiking, geology tour, or pub crawl, and suggestions are welcome. You're responsible for travel to and from Ithaca, but you're welcome to stay with me in my historic grad student Co-op house (schedule permitting), and I can provide local transport. Must visit before May 2016.
\subsection{Help with fellowship/grad school/research internship apps!}
Jeff Holzgrafe and Brendan Quinlivan
\\
Starting Bid: \$10
\newline
Do you wonder why engineering grad programs make you write with words and sentence structure and paragraphs like some kind of high-school-aged essay writing person? (Do you use sentences like that one?) Are you yearning for the American tax payer to fund your education???

Let us give you a hand! We can edit fellowship essays, talk you through grad school visits, chat about the application process, or  help you think about your future life in higher academics. We'll give you an hour of our eyeballs for every \$10 you spend! You can trust us: we got Uncle Sam to fork over the \$\$\$ twice!
\subsection{3D print your stuff! }
Larissa Little
\\
Starting Bid: \$10
\newline
I've been working at Formlabs as a materials engineer for a while now. As a results, I know a lot about 3D printing in general and also have access to printers 24/7. 

If you win, I'll 3d print a model of your choosing on a Formlabs printer and deliver it to you!

If bidding goes over \$15 I'll also give you design tips and explanations of the process. 

If bidding goes over \$20 and you're interested, I'll take you out to brunch (or skype you if you're not Boston local) where I will really enthusiastically talk about 3D printing and try to answer any questions you have about the process or the industry. I will be extra enthusiastic if we talk about materials :D
\subsection{I will make YOU into a DJ}
Scott Mackinlay
\\
Starting Bid: \$10
\newline
For at least an hour, or until a party spontaneously breaks out, I will do my best to turn you into a world class DJ.
\subsection{Babysitting }
Nicole Rifkin
\\
Starting Bid: \$15
\newline
\$15 per babysitting hour (i.e. a \$30 donation = 2 hours)
Can be spread out however you like, redeemable any time before May 2016
\subsection{Finals Care Package}
Jenn Simonovich ('12)
\\
Starting Bid: \$15
\newline
I will send you a finals care package! I have lots of experience in this area, both on the receiving end when I was at Olin, and on the sending end to my little sister in college. Expect delicious snacks, homemade baked goods, small cute knitted or crocheted items, pictures of my kitties, tea, and other feel-good things TBD. Available only for this school year, but your choice of winter or spring semester.
\subsection{San Francisco housing hunt help}
Ilana Walder-Biesanz
\\
Starting Bid: \$20
\newline
Moving to San Francisco? Need someone to look at housing options? I will attend up to three open houses (schedule permitting, but I'll do my very best to get to the ones you want) for you and send you a report on what I see. (You can of course send me a list of specific things to look for, if you have particular preferences.) That number increases to five if the winning bid is greater than \$60.
\subsection{IT services}
Dhash
\\
Starting Bid: \$20
\newline
You get 10 instances of having me help you with IT stuff, from configuring your router so Mike Horne will not track you down and order the AP's to kill your router, to tech advice about the latest and greatest gadget to buy for your mother.
\subsection{Life Advice Care Package}
Nikki Lee \& Jeffrey Atkinson
\\
Starting Bid: \$20
\newline
With their combined 3 degrees, 5 years of PM experience, and 137 inches of height, Jeffkinson ('12) and Nikki ('10) have a lot to offer you.

In particular, they are offering to send you a care package. A care package of life advice.

What exactly is a care a package of life advice? They aren't quite sure yet, but whatever it is will be great. It will probably contain both care and life advice, and most likely something edible from Seattle. You can trust them. They're alumni. Alumni are trustworthy.

* Winner will be asked to provide a list of food allergies, phobias, and celebrity crushes in the interest of safety.
\subsection{Making a trip to East Africa easy!}
Erin McCusker
\\
Starting Bid: \$25
\newline
East Africa (Particularly Kenya and Rwanda)  is beautiful and exciting! What an adventure! ....and that's just the immigration line....

Your donation can purchase a streamlined advisory service including tips and tricks on booking flights, highlights to be sure to include (based on my knowledge), recommended hotels/ safaris/ etc, and safety tips. Make the adventure way less intimidating and come experience it!
\subsection{So You Wanna Work in Video Games...}
Brian Shih
\\
Starting Bid: \$25
\newline
My name is Brian, I graduated in '07, I've been working at a mobile gaming company as a PM for 4 years and was a PM at Google before that. I can talk to you about what it's like making games, game design theory, games to play and product management that's specific to making games. If you love playing games and have ever wondered about working in games, I would love to talk to you.
\subsection{Custom Superhero Cape}
Sylvie Stacy
\\
Starting Bid: \$30
\newline
I will sew a spectacular superhero cape for you. It can be the colors, fabric, trimmings, logo, and size that you choose. Alternatively, if you’re more practical than whimsical, I can make you a functional, cozy, wear-it-about-town cape.
\subsection{Stay in our San Francisco home!}
Jenn Simonovich ('12), Celeste Maisel ('13.5), and Karl Schults ('11)
\\
Starting Bid: \$30
\newline
Jenn Simonovich ('12), Celeste Maisel ('13.5), and Karl Schults ('11) have a cute little home in the Sunset District of San Francisco. Stay with us in our guest bedroom for up to 3 nights. Our house is right near public transit, 10 blocks from the beach, ~1 mile from Golden Gate Park, around the block from nationally-ranked Chinese restaurants, and has lots of available parking. We'll feed you delicious food, show you around the neighbourhood, and hang out with you and our two adorable cats and one adorable golden retriever. This item pairs nicely with the tour of Instructables led by Celeste.
\subsection{Career Coaching - three 30min sessions}
Lindsay Gordon
\\
Starting Bid: \$40
\newline
I graduated in 2007, currently live in San Francisco and have been with Google for 5.5 years. At work I'm responsible for the career development of ~60 people globally and in my free time I run my own coaching business. 

I'd like to offer you three 30 minute career coaching sessions where I can help you make changes in your current job, figure out a new career or help you think through any other career related situations. I have several exercises that I do with clients that can help you learn your own strengths, values, happiness in your current role, etc. Check out some testimonials at lindsaygordon.com/coaching-testimonials.

Value is \$225 and I look forward to working with you!
\section{Miscellaneous}
\subsection{Robbie Siegel}
Andrew Deaver
\\
Starting Bid: \$0.01
\newline
I received Robbie as a gift from the Gods. Despite his chiseled body and unearthly good looks, I'm not quite sure what he's good for. As far as I can tell, he requires regular sustenance to remain functioning. Please find him a good home. As for winning this auction, I'm not quite sure what you win when you receive Robbie... nor do I really know what it means to be in possession of Robbie.
\subsection{Literally Nothing}
Alexander Crease
\\
Starting Bid: \$0.01
\newline
With certificate
\subsection{yep}
Doyung
\\
Starting Bid: \$0.01\$
\newline
mhm.
\subsection{Any other item in the SERV Auction}
Doyung and Shane
\\
Starting Bid: \$0.5
\newline
Win this item. Choose any other item in the SERV Auction and we will do that for you EXCEPT we will match the quality/effort to what you pay for this item. 

Win this for 1 dollar and ask for resume help, I dare you. Just watch what happens.
\subsection{Do you hate Linnea's hair?}
Linnea Laux
\\
Starting Bid: \$1.00
\newline
Are you sick of Linnea's hair? So is Linnea. For every \$10 the Olin community donates, another centimeter will be cut off. This is limited to the amount of hair I currently have.
\subsection{Postcards from Mali + More}
Caroline Condon ('13)
\\
Starting Bid: \$1
\newline
A postcard from Mali. With a pretty picture, a note, and presumably a cool stamp. 

Bonus postcards from any countries that I have enough layover time to leave the airport in. I don't know which these will be so they'll be a surprise!
\subsection{Box of Socks from Korea}
Kat Kim (Alumna '07)
\\
Starting Bid: \$1
\newline
I live in Korea and they make the cutest socks! The winner of this auction will be mailed a box of super-cute Korean socks. I will send at least 5 pairs, but, really, I will send as many as I can fit in a small box. Bid now and your feet will thank you later.
\subsection{Olin Pokemon League Sell Out}
Mitch and Alex
\\
Starting Bid: \$1
\newline
Do you want to become the very best, that no one ever was? For the low cost of the winning bid, you will become a Gym Leader of the historic and famous Franklin W. Olin Pokemon League, a group of only the toughest, smartest, most epic Pokemon Masters in the Olin Region (but don't worry, if you don't want to put that much effort into it, you can be one of the easier Gym Leaders). You and your Pokemon will battle challengers and protect the world from devastation. You will travel across the land, searching far and wide, each pokemon to understand, the power that's inside.
\subsection{Check if you are getting all students}
Saarth Mehrotra
\\
Starting Bid: \$1
\newline
Ill make sure that you are getting all student emails!
\subsection{TBD}
Jaime Grau
\\
Starting Bid: \$1
\newline
I don't know yet, but I guarantee a very fun time!
\subsection{maggie su}
janie
\\
Starting Bid: \$1
\newline
this is for maggie.  If you don't know her you should.  you can hang out with her for a day and do fun things.  I suggest pancake art or dumpster diving or soap carving. Or you can make pot stickers.  I will be there as well.  her favorite vegetable is broccoli and she likes to catch frisbees. This can be at my house or hers, she does not know about this.
\subsection{Antarctic Thing}
Philip Chung
\\
Starting Bid: \$1
\newline
You are bidding on a thing from Antarctica. I haven't decided what, yet. Delivery in May 2016.
\subsection{Make you a "Dank" Playlist}
Saarth and Doyung
\\
Starting Bid: \$1
\newline
We will make you a playlist for the ages... It's like a modern mixtape!
\subsection{Send You Interesting Articles}
Anne LoVerso
\\
Starting Bid: \$1
\newline
Sometimes I read interesting articles on the internet, and when I find one particularly interesting, I'll send it to you.  You can request specific topics you like if you want.  Mails will occur at a frequency of whenever I find something that's interesting, for a duration of 1 week per dollar donated, or until you find it annoying and tell me to stop
\subsection{Angsty Walk Through Parcel B}
Anne LoVerso
\\
Starting Bid: \$1
\newline
If you message me at any time of day (when I am not already asleep) (or in class), we will go on a walk through Parcel B.  We can either talk about our angsty feelings, or we can just be silent and angsty together.  Your choice.  Good for one angst walk
\subsection{Buy You Something Interesting}
Anne LoVerso
\\
Starting Bid: \$1
\newline
I'll buy you something interesting, the value of which will be equivalent to the winning bid
\subsection{Iamb What Iamb}
Harold Jaffe
\\
Starting Bid: \$1
\newline
I'll write for you a sonnet on your choice of subject or to fit your chosen theme. While strict poetic formulae may seem archaic, they are able to give voice to feelings and ideas of any time. Just specify a topic or compile a list of key words to be used, and I'll elaborate on them in metered rhyme!

For further information, please feel free to get in touch. I'm happy to provide some samples of my work so you can see the sort of poem you'd be buying. I'd say talk to Jacob Miller (Mr. T) or Pudlo if you want the buyer's side.
\subsection{2nd Place in the 2015 SERV Auction}
SERV Auction Committee
\\
Starting Bid: \$1
\newline
Winning the SERV Auction can be a little much for some people. Get this item to claim 2nd place in this year's SERV Auction. If bidding goes over \$5, you can have retroactive 2nd place in last year's auction, too. If bidding goes above \$10, I'll make you a trophy, but be sure to lower your expectations.
\subsection{Express your opinions}
Josh Langowitz
\\
Starting Bid: \$1
\newline
I will sit down and have a conversation with you about a topic of your choice and then share your opinion as if it were my own, depending on the amount of your bid:
\textless \$5 - we talk for half an hour, and the next time I am in the dining hall, I start a conversation with whoever I eat with on the topic and take your opinion in the conversation
\textless \$10 - we talk for up to an hour, and I send an email containing my interpretation of your opinion to an individual of your choice, containing at least 500 words.
\textless \$20 - same as \$10 except I email up to 5 people and use 1000 words.
\textless \$30 - same as \$20 except I email an entire class list.
\textless \$40 - same as \$20 except all students.
\textless \$50 - same as \$40 except I express your opinion in video form.
\textless \$100 - \$50 and I express your opinion in my 15 words at graduation as well.
\$100+ - same as \$100 except the video is done as a character or impression of your choice (I'll put a good faith effort into being able to pull of the character/impression decently well).
\subsection{Nothing!}
Josh Langowitz
\\
Starting Bid: \$1
\newline
Do you need to ask?
\subsection{Mystery SERV Auction Item}
Josh Langowitz
\\
Starting Bid: \$1
\newline
The winner of the "Choose a Mystery SERV Auction Item" item will decide what you get.
\subsection{Choose a Mystery SERV Auction Item}
Josh Langowitz
\\
Starting Bid: \$1
\newline
Sit down with me and decide what I will give to the winner of the "Mystery SERV Auction Item" item. I reserve the right to veto anything that I consider of lower value than the winning bid on this item.
\subsection{This is the first puzzle in the puzzle hunt}
Josh Langowitz
\\
Starting Bid: \$1
\newline
Aol zljvuk wbggsl pz aol palt apaslk Dhajo fvby mhcvypal tvcpl hz P ayf av wvpua vba aol ihk wofzpjz. Winning bid gets a clue as to how to solve this, assuming nobody has finished it before the auction closes.
\subsection{Rage Walk}
Josh Langowitz
\\
Starting Bid: \$1
\newline
At 1 dollar, I will walk with you through Parcel B and listen to you complain to me about whatever you are angry about.
At 1 dollar, this walk will last up to 15 minutes.
At 2 dollars, this walk will last up to 30 minutes.
At 3 dollars, I will drive you to 711 and buy you a slurpie and listen to you complain to me about whatever you are angry about.
At 5 dollars, I will try to help.
At 8 dollars, I will NOT try to help.
At 13 dollars, in addition to a slurpie I will buy us each a pint of ice cream and we will eat them and optional cry about whatever you are angry about. After we go through this process, we will have solved all of your anger problems, because ice cream makes things better.
\subsection{Exclusive The Cutest Rights}
Nicole Rifkin
\\
Starting Bid: \$1
\newline
Ever wanted to be The Cutest? For some period of time, you will have exclusive The Cutest rights. I will call nobody but you the cutest, and aggressively and publicly remind you just how The Cutest you are. Amount of time is proportional to the size of the bid.
\subsection{Gifts for a year}
Shane, Doyung and Adam
\\
Starting Bid: \$1
\newline
So this item is a little weird. Read this note: You're expected to pay your highest bid, but that does not mean you will get the item. 
Intrigued?  Read on.
This item is won via raffle. Every single person who bids on this item is entered into a raffle. The number of tickets each person has in the raffle is equal to the largest amount of money they have bid, where \$1 = 1 ticket. Everyone is expected to pay their highest bid. We will then draw a name. This person will receive a surprise number of presents (more than 2) from us in the mail throughout the next 365 days. The gifts will be worth at least \$100 total.
For each \$50 being donated beyond \$100 total, we will pick another name from the raffle and send them a single cool gift at a random point in the next 3 months without telling them.  
You must bid in whole number increments. 
You can not cross out your name.
\subsection{Three lovely pieces of mail}
Becky Belisle
\\
Starting Bid: \$2
\newline
Three letters, postcards or small packages from Becky Belisle ('10) to you, at three different times during the year. Mail is likely to include funny drawings, poems, pontificating about nothing in particular, and facts about the best places to have picnics in the state of California. At least one will be written on top of a mountain.
\subsection{Afternoon with cats! }
Tiana Veldwisch '08
\\
Starting Bid: \$2
\newline
New and improved from last year: we have added a third and even more playful cat to the mix. Do you miss your kitties at home? Come play or cuddle with our cats! Conveniently located near Davis square; subject to scheduling at mutually convenient time. We'll even provide snacks/cat treats /tea.
\subsection{Your Face in an R2 Room}
R2 Team
\\
Starting Bid: \$2
\newline
Each R2 will hang a picture of your face in their room
\subsection{R2 surprise}
R2 Team
\\
Starting Bid: \$2
\newline
It's a surprise!
\subsection{4 Skip the line passes!}
the ACRONYM
\\
Starting Bid: \$2
\newline
Have you ever come to the ACRONYM but the line is too long? Win this item for 4 passes to instantly skip to the front of the line to get your coffee or tea right away!
\subsection{Exclusive Hugging Rights}
Celina Bekins
\\
Starting Bid: \$4
\newline
For every \$4 you donate, you get half an hour of being the only person I am allowed to hug. This means you get as many hugs as you want (as long as you're not keeping me from class or anything)! And I can't hug anyone else during that time. Your time being the sole recipient of my hugs will begin the day after the auction closes, at an hour we'll settle on together.
\subsection{Yodeling swag}
Ilana Walder-Biesanz
\\
Starting Bid: \$5
\newline
At Yahoo, we yodel. If you win this item, I will get you every piece of yodeling swag the company store offers. This will include a yodeling bottle opener, a yodel button, a yodeling greeting card, and possibly other things I am forgetting. Be afraid.
\subsection{Pick my next hair color!}
Tatiana Anthony
\\
Starting Bid: \$5
\newline
Brown, (briefly blonde), blue, pink, purple, and red.  That's what I've had for my hair so far.  You get to pick my next hair color!  I'll dye it over Thanksgiving break, and I'll keep it at least until the end of the semester.
\subsection{Puzzle You Can Solve}
Philip Z Loh
\\
Starting Bid: \$5
\newline
I'll write you a puzzle you can solve! If you can't solve it, I'll keep writing new ones until you can!
\subsection{Puzzle You Can't Solve}
Philip Z Loh
\\
Starting Bid: \$5
\newline
I'll write you a puzzle you can't solve! If you can solve it, I'll keep writing new ones until you can't!
\subsection{Your Name (or Something Else You Want) in a National Puzzle Contest}
Philip Z Loh
\\
Starting Bid: \$5
\newline
I'm writing puzzles for the Microsoft College Puzzle Challenge 2016. You get to decide on one SFW, reasonable thing for me to include in a puzzle! Of course, you won't get to see it until the puzzle challenge happens (you're highly recommended to participate)...
\subsection{A Microsoft Interview}
Philip Z Loh
\\
Starting Bid: \$5
\newline
I will call you from work with Skype for Business(TM) and ask you about your life story. Optional: I'll take notes with OneNote(TM) if you want.
\subsection{Tell you what you need to know about Burning Man}
Graham Hooton
\\
Starting Bid: \$5
\newline
I went to Burning Man in the Black Rock desert this year. It was life-altering. If you're thinking about going, you should go. If you're not thinking about going, you should think about going.

My sister helped me through the whole process of buying tickets, preparing supplies, etc. etc. etc. It's complicated, and I don't know if I could have done it without her. 

If you win this item, I'll make sure you know everything you need to about going to Burning Man. And who knows, maybe I'll see you there next year!
\subsection{Pen pals for life}
Graham Hooton
\\
Starting Bid: \$5
\newline
It's nice to receive mail! It's nice to keep in touch with old friends!

The winner of this item will receive one letter, and the guarantee that if they ever send me a letter in the future, I will send them a reply.
\subsection{Juicebox and Chill}
Deborah H
\\
Starting Bid: \$5
\newline
I bring the juicebox, you bring the chill. Contents of juicebox negotiable.
\subsection{Talk about Life Cafe}
Kai Austin
\\
Starting Bid: \$5
\newline
I will take you out to any cafe of your choice for coffee, tea, lemonade, or variations there of and we will talk about life, Olin, life before Olin, life at Olin, life after Olin, life without any mention of or relation to Olin, or whatever life/living related thing you want to talk about.
\subsection{Talk about Death Cafe}
Kai Austin
\\
Starting Bid: \$5
\newline
I will take you out to a cafe of your choice for coffee, tea, lemonade, or variations there of and we will talk about death*. No idea why you would want to talk about death, but I tend to be uncomfortably enthusiastic about it so feel free to get as taboo as you wish.

* Death as in the subject. If you are grieving loss, seeking spiritual comfort, or need to dispose of a body, please bid elsewhere.
\subsection{Banjo Serenade}
Meg Lidrbauch
\\
Starting Bid: \$5
\newline
Have you ever wanted to hear the sweet, sweet sound of a banjo as played by a beginner? Well, you're in luck! I will play BOTH songs that I know for you. If the winning bid is over \$10, I'll even try to pick out a song or two of your choice by ear.
\subsection{Hug animal loan}
Mel Chua
\\
Starting Bid: \$5
\newline
Strunkenwhite the Giant Teddy Bear, Fritz the Penguin Hat, OR Hug Panda the Shoulder Wrap will be yours to take around and bring home for as many days as \$your\_bid/5 (so: \$5 gets you 1 day of hug animal loan, \$10 gets you 2 days, \$15 gets you 3, etc.)

Top bidder gets first pick of hugging animal; second bidder gets the remaining two.
\subsection{Horror Movie with Wimps}
Daniel L, Saarth M, Searing
\\
Starting Bid: \$5
\newline
We're TERRIFIED of horror movies. Daniel has watched exactly one in his life and couldn't sleep for two days afterwards, Saarth gets physically ill when he watches them, and Searing finds them generally unpleasant. Win this item and you can make all three of us watch one horror movie of your choice while watching us freak out.
\subsection{Package from Vegas}
Jennifer Wei
\\
Starting Bid: \$5
\newline
I'll send you a mysterious package from Vegas (or at least filled with items from Vegas) when I go in January! The higher the bid, the less cruddy (and possibly larger) the package.
\subsection{Tell me about yourself}
Josh Langowitz
\\
Starting Bid: \$5
\newline
I will talk to you for up to an hour as you tell me about yourself. I will make insightful comments about your life and/or question your choices if you so choose.
\subsection{Tell you about myself}
Josh Langowitz
\\
Starting Bid: \$5
\newline
I will talk to you for up to an hour and tell you about myself. You will make insightful comments about my life and/or question my choices if you so choose.
\subsection{Tell you about yourself}
Josh Langowitz
\\
Starting Bid: \$5
\newline
I will talk to you for up to an hour as I tell you about yourself. I will make up assorted details about your life and you can guide and correct me as much as you choose.
\subsection{Tell me about myself}
Josh Langowitz
\\
Starting Bid: \$5
\newline
I will talk to you for up to an hour as you tell me about myself. I will guide you to conclusions about myself that may or may not be the truth if you so choose.
\subsection{Something From Long Beach, California}
Lauren Froschauer
\\
Starting Bid: \$5
\newline
A surprise from Long Beach! 
The more you pay, the fancier it gets!
\subsection{International Video Conference}
Ryan Louie, Emily Wang
\\
Starting Bid: \$5
\newline
Have a Google Hangout with Emily in Needham and Ryan in Singapore! Includes an optional virtual tour of either location. 

Must be claimed sometime in the Spring 2016 semester!
\subsection{FWOP Tickets for Life (1/2)}
Philip Z Loh
\\
Starting Bid: \$10
\newline
For as long as: (1) You live, (2) I live, and (3) FWOP is around, I will buy your FWOP tickets (limit 1 per production) so all you have to do is simply attend and enjoy the amazing feeling of royalty. If this gets above \$100, I might even throw in some intermission snacks -- that's beyond royalty!
\subsection{FWOP Tickets for Life (2/2)}
Philip Z Loh
\\
Starting Bid: \$10
\newline
For as long as: (1) You live, (2) I live, and (3) FWOP is around, I will buy your FWOP tickets (limit 1 per production) so all you have to do is simply attend and enjoy the amazing feeling of royalty. If this gets above \$100, I might even throw in some intermission snacks -- that's beyond royalty!
\subsection{Something from Copenhagen/Europe}
Meg Lidrbauch
\\
Starting Bid: \$10
\newline
Next semester I will be studying in Copenhagen. As such, I will buy the winning bidder something from Copenhagen or my other travels through Europe worth the winning bid amount + USD 5.00. The object will be anything I find amusing/pretty/cool unless you have a very specific request, and even still I might just buy something random.
\subsection{Shave my head!}
Katie Butler
\\
Starting Bid: \$15
\newline
For \$15 I will let you shave the already shaven part of my head
For \$20 you can put a design in it
For \$50 you can shave further (details tbd)
For \$100 you can cut//shave my head (details tbd)
\subsection{Facebook "Red Type" Poster}
Greg Marra, Chris Marra, Scott Thomson, Patrick Varin, Alyssa Levitz
\\
Starting Bid: \$15
\newline
We will get you an inspirational poster hand printed by the Facebook Analog Research Lab. Search "Facebook red type poster" to see examples. Exact quote will depend on what is available. If the bidding passes \$75, we will also frame it for you.
\subsection{Watch me eat a Vermonster}
Josh Langowitz
\\
Starting Bid: \$80
\newline
I will try to eat a Vermonster by myself (I buy the Vermonster). I will go to Ben and Jerry's, purchase it, bring it back to Olin, place it in a larger bucket full of ice, and proceed to eat it over the course of the day. You can film this process, take pictures, taunt, encourage, or discourage me at your leisure. After I eat the Vermonster, I will clean the bucket and wear it on my head in triumph for the entirety of the next day. In the event that I fail to finish the Vermonster after a 24 hour period of starting it, I will NOT clean the bucket and wear it on my head in shame for 1 hour.
\subsection{Win the SERV Auction Puzzle Hunt}
Josh Langowitz
\\
Starting Bid: \$1337
\newline
There are secret clues hidden in my other SERV auction items. Whoever emails me with the correct answer to the puzzle hunt therein wins a prize. Whoever wins the bidding on this item probably shouldn't have bid over a thousand dollars for nothing.
\section{Faculty and Staff}
\subsection{Art work from Build Day}
Academic Affairs
\\
Starting Bid: \$3
\newline
These sixteen paintings were created during the first Build Day event.  The painters each expressed themselves through art.....and one of these creations could be yours!
\subsection{Cover Letter}
Sally Phelps
\\
Starting Bid: \$5
\newline
You no longer need to be INTIMIDATED by that cover letter you have to write.  Sally will write a killer cover letter for you for the job of your dreams!
\subsection{Strudel Making Lesson}
Emily Petersell
\\
Starting Bid: \$5.00
\newline
We will make authentic Austrian strudel from scratch together using my grandmother's recipe--and eat it afterward! The strudel is vegetarian but not vegan.
\subsection{Portfolio/Web Site Advice}
Sara Hendren
\\
Starting Bid: \$5
\newline
Want another set of eyes on your web site, especially on your bio paragraph, or on the language you use in your portfolio? I've done a lot of "doctoring" on these kinds of documents. We can sit for an hour and brainstorm if you're starting from scratch, or try to shape what you have already. The top 3 bidders will win and each receive this item.
\subsection{Something Awesome, 10 Years From Now}
Matt Ritter
\\
Starting Bid: \$10
\newline
A flying car? A retro-rickroll? An antique iPhone? Thanks to several different email reminders

that will be blasting my and my familys email addresses in 9.5 years, I will be prepared to deliver Something Awesome on the decennial anniversary of the prize announcement.

”The best way to predict the future is to create it, by winning the SERV auction” - Peter Drucker
(edited for completeness)
\subsection{Yoga with Sally}
Sally Phelps
\\
Starting Bid: \$10
\newline
Bring two friends and enjoy 2   1-hour sessions of vinyasa yoga with Sally Phelps at a mutually convenient time.  Sally will adapt to your level of yoga.  

Or you can just do shivasana for an hour – always enjoyable.
\subsection{Horizon Hobby Mini Vapor, Ready to Fly!}
Andrew Bennett
\\
Starting Bid: \$10
\newline
Dominate the airspace over the couch!  Be the ace of the dining hall!  The Mini Vapor from Horizon Hobbies is a tiny, lightweight, indoor radio controlled airplane. The tiny ParkZone® Mini Vapor® slow flyer is the ideal indoor flyer for those who don’t have a lot of room to fly indoors. Its precise 3-channel control, slow speed and light weight make it possible to navigate spaces as small as a bedroom or kitchen without bumping into a thing.
\subsection{Boston Marathon Volunteer!}
Alison Black
\\
Starting Bid: \$10.00
\newline
Come volunteer with me at the world-famous Boston Marathon!  Every year I am somewhere along the course watching a clock.  We can decide which part of the course we want to be on.  It's a long day but very fun (it's always on Patriots Day which is the third Monday in April--no school that day).  We have a great viewing spot for the marathon, and we get a FREE Adidas volunteer jacket that is worth around \$85.00.  If you haven't volunteered for the Boston Marathon, then.....
\subsection{WEGMAN'S!}
Alison Black
\\
Starting Bid: \$10.00
\newline
Let's go to the brand new Wegman's in Westwood!  If you haven't been to Wegman's then you are in for a treat!  This trip is for you and a friend and will include lunch.  Once you see this new Wegman's, you may never want to leave.  It's a grocery store but SO MUCH MORE!!!  Just ask Hannah Wilk.
\subsection{8oz jar of Olin honey}
Parcel Bees, Benjamin Linder advisor
\\
Starting Bid: \$10
\newline
The Sustainable Beekeeping co-curricular runs Parcel Bees, a honey CSA (Community Supported Agriculture) for Olin alums, who pay for a seasonal share and receive honey harvested on campus.

You are bidding on an 8oz jar of Olin honey. The top 4 bidders will receive one 8oz jar each. This is the only way to get Olin honey if you are not a member of the co-curricular or a shareholding alum in Parcel Bees!
\subsection{ceramics}
mark somerville
\\
Starting Bid: \$10
\newline
Mark will make you SOMETHING out of clay.  The scale, function, customizability, and decoration of said item are dependent on the level of bidding that this item reaches.

Note: I will make mugs for *all* bidders above \$25, and something custom for all bidders above \$75.
\subsection{Dish Garden}
Vivien  Bouffard
\\
Starting Bid: \$10
\newline
Small dish garden in a handmade pot thrown in the Babson Ceramics Studio.  Plants are semi-guaranteed to live even in a dorm room.  For awhile, at least.
\subsection{Movie Night in my aparment}
A.J. 
\\
Starting Bid: \$15
\newline
You get access to my living room and T.V. with its couches and window shelf. Bring snacks and friends and watch a movie of your choice in my living room for the evening. With me or without me, your choice. This item is won by the first bidder and second bidder.
\subsection{Sushi Lunch w/Marketing \& Communication}
Marketing \& Communication
\\
Starting Bid: \$15
\newline
Please join the Marketing \& Communication team (Michelle Davis, Joe Hunter, Alyson Goodrow, Anne-Marie Dorning + Sarah Pickering) for a lunch of sushi, sushi and more sushi! YUM
\subsection{Thanksgiving Dinner with the Harris'}
Scott \& Jody Harris
\\
Starting Bid: \$20
\newline
Scott \& Jody Harris
Starting Bid: \$20
Are you stranded on campus this Thanksgiving? Is your mom a terrible cook? Here is a chance to have Thanksgiving dinner with us and our whacky neighbors and anyone else that drops by. Join us for some amazing food. Ask anyone who has eaten at our house... Jody is a fantastic cook and nobody leaves hungry.

On Thanksgiving day, I will pick you up (if you do not have a car) and bring you to our house in Acton for a GIANT meal. You will be an honorary member of my weird family for the day. We may even do some mad science (ask Dakota, Liani or Sarah). There will also be an optional hike in the woods between dinner and desert. Last year our hike turned into an epic snow-ball fight (FYI - Liani can whip a snowball like nobody's business).

I will drop you back at Olin in the evening.

We can accommodate up to 4 people with winning bids (or 7 if some can provide their own transportation).
\subsection{Kayak Outing}
Scott \& Jody Harris
\\
Starting Bid: \$20
\newline
Jody and I will take you out on a kayak adventure. We will supply transportation, boats, instruc- tion, safety equipment, gourmet lunch/snacks and guide service on a local river. We will paddle 3 to 7 miles (whatever distance you are comfortable with) and return you safely to Olin.
We can accommodate up to three people (each bid separately). Weather permitting... we will go out this year, but we may have to wait until spring.
\subsection{End of Semester Stress Reduction Basket}
Rae-Anne Butera
\\
Starting Bid: \$20
\newline
By winning this item you will be the recipient of a basket full of goodies curated just for you to help reduce your end of semester stress and anxiety. Think comfort and relaxation!
\subsection{It’s Like Having Mom Here}
Financial Affairs 
\\
Starting Bid: \$20
\newline
Homesick?  Or maybe you just need a little extra TLC.  A group of Financial Affairs Moms are willing to adopt you for the rest of the school year.  We will send you a minimum of 4 care packages at random times, possibly send you an occasional card, and are willing to e-mail, text, or personally deliver words of encouragement (only with your consent).  Of course we might have to offer you the occasional Mom-ism, just to make the whole experience authentic.
\subsection{Ride Along with BABO}
Olin Public Safety
\\
Starting Bid: \$20
\newline
Be a part of the Olin Public Safety team for a day!  Come spend up to 4 hours riding along with the Police Officers.  Start with a tour of the Police Station and head out on the road with us.  We always look forward to spending time with our Olin community.  Date and time of the ride along will be determined based upon the highest bidder's availability.
\subsection{The Perfect Resume}
Sally Phelps
\\
Starting Bid: \$25
\newline
Sally will write a fantastic resume for you FROM SCRATCH!  She will also help you source leads and prepare for your interview.
\subsection{Hot Chocolate Tour}
Alexandra Strong
\\
Starting Bid: \$25
\newline
Winter is coming, and that means hot chocolate! You and two friends will join me and my husband for a hot chocolate tour of Boston. We will stop at 3 places to sample different hot cocca styles - from Burdick's in Harvard Square for drinking chocolate to Simon's Coffee Shop in Porter for Mexican Hot Chocolate to Paris Creperie for Nutella hot chocolate. (If you have another favorite hot cocoa spot, we can definitely consider that as well!)
\subsection{Pizza + Bowling!}
Jeff Beck, Miranda Bethune, Jeremy Goodman, Alyson Goodrow, Shannon Paleologos, Sarah Pickering, Krissy Raposa
\\
Starting Bid: \$25
\newline
We will treat you and 6 of your friends (so 7 people total + the 7 of us) to a fantastic evening of pizza at Hearth and bowling at Needham Bowlaway. We'll work together to arrange a day and time that everyone is amenable to. Things might get a little competitive and just a little crazy. Let's face it, this will cost us a lot more than the minimum bid, so the higher the bid, the more bowling we'll do. If bidding goes above \$50, Sarah will tell you a joke. If bidding goes above \$60, Alyson will give you some awesome style tips. If bidding goes above \$70, Krissy will give you party planning advice.  If bidding goes above \$80, Miranda will sing to you.  If bidding goes above \$90, Jeff will play the saxophone.  If bidding goes above \$100, Jeremy will perform as much of a Shakespearean monologue as he can remember.  If bidding goes  above \$110, Shannon will surprise you (with what? it's a surprise!). If bidding goes over \$250, the whole group will do improv games for your entertainment.
\subsection{Hand-made tea pot and mugs}
mark somerville
\\
Starting Bid: \$25
\newline
Own an original Somerville Ceramic piece.  Or three, actually: a teapot and two matching mugs can be yours,*if* the price is right.
\subsection{30 minutes Mandarin Chinese tutoring}
Zhaopeng Ji
\\
Starting Bid: \$30
\newline
Want to impress your friends with some Chinese characters, even Calligraphy? Want to order your beloved Chinese food in Chinese? Want to learn some conversations in Chinese? Want some help with your Chinese homework? I can be your help. Together, we will make this 30 minutes session well spent!
\subsection{Ice Cream and Advice}
Maruta Vitols
\\
Starting Bid: \$30
\newline
Do you love ice cream? Do you need advice? Do want a trip to the magical land of Cabot's Ice Cream in Newton? If you answered yes to these questions, then this is the item for you! Be the highest bidder and win a trip to Cabots for yourself and two of your buddies with Maruta! You'll be able to have deep philosophical discussions while indulging in sundaes the size of your head. Receive priceless advice from Maruta while devouring enough ice cream to send a pony into diabetic shock. Let's face it: life is better with sprinkles....
\subsection{Let's make pizza at my house!}
Aaron Hoover
\\
Starting Bid: \$30
\newline
I'm serious about pizza, and you should be too. You and up to five of your friends are invited to my house for a night of epic pizza making and eating. I'll provide home made dough, some classic fresh toppings (entirely customizable by you), and age-appropriate beverages. You bring the stimulating conversation and a willingness to make a fool of yourself tossing pizza dough in the air.
\subsection{2 Red Sox Tickets}
Sharon Woodward
\\
Starting Bid: \$30
\newline
2 Red Sox tickets, Grandstand Section 8, aisle seats for a game in April or May 2016.  Date of game TBD with winner at the end of March 2016.
\subsection{Walk down Lactose and Literature Lane}
Mel Chua
\\
Starting Bid: \$50
\newline
What better way to spend a fall (or spring) weekend day than walking around Camberville partaking of gourmet ice cream and froyo and stopping by little bookshops on the way? Mel Chua will guide up to 4 people on a walking tour of her favorite ice cream and book spots (all roughly on the way from MIT to Harvard). Potential stops include Toscanini's, Christina's, JP Licks, the MIT Press Bookstore, Rodney's, Schoenhof's (foreign language bookstore), the Curious George bookstore, and more.

One ice cream item per person per stop is included in the bid, along with copious amounts of Lactaid will be provided for lactose-intolerant people like Mel. (You'll need to pay for any books you buy.) Transport to/from Olin available if needed.
\subsection{beverage tasting}
mark somerville
\\
Starting Bid: \$50
\newline
At some point in your life, you come to appreciate that beverages are best enjoyed in small, but high quality, quantities.  We will collaboratively select a beverage genre of your choosing, and then Mark will arrange appropriate examples of said genre, with appropriate associated comestibles to compliment the genre.

Depending on the choice of genre, other faculty members will be recruited to assist.  John Geddes, for example, is of a Scotsman (despite his recent adoption of the red white and blue) so he might be an appropriate host if we chose to taste bad soda.
\subsection{Baking with Jessica and Abby}
Jessica Townsend
\\
Starting Bid: \$60
\newline
(This is for a group of up to 6 people). Come have a baking extravaganza at my house in lovely Union Square, Somerville. I will provide all baking ingredients, equipment and rations (from a local Somerville take-out place). You provide the recipes and inspiration and develop a plan to complete substantial baking projects in a mere 4 hours. Abby the dog will act as chief tail-wagging supervisor and will run the clean-up crew.
\subsection{High Heels: Running, Walking, and Crawling}
Zhenya
\\
Starting Bid: \$100
\newline
This highly intensive, highly hilarious, highly physical class will teach you the art of moving on high heels. I have no experience teaching such things and neither do you need any experience.  Bring your heels or your friends' heels or your friends' friends' heels and let's have some fun! (You may want to bring helmets, as well as knee and elbow pads... just in case :) ).

Minimum class size: 5 people
\end{document}
