\documentclass[11pt]{article}
\pagestyle{plain} \topmargin -.5in \oddsidemargin 0in
\evensidemargin 0in \textwidth 6.5in \textheight 8in
\setlength{\parindent}{0in}
\title{Live Auction Donation Packet}
\author{SERV Auction 2016}
\date{November 7th, 2016 to November 11th, 2016}
\begin{document}
\maketitle
\subsection{Item Title}
Donor Name(s)
\\
Starting Bid: \$Item Starting Bid
\newline
Item Description
\subsection{Thanksgiving Dinner (and mad science) with the Harris'}
Scott \& Jody Harris
\\
Starting Bid: \$20
\newline
Are you stranded on campus this Thanksgiving? Is your mom a terrible cook? Here is a chance to have Thanksgiving dinner with our family and our whacky friends and anyone else that drops by. Join us for some amazing food. Ask anyone who has eaten at our house... Jody is a fantastic cook and nobody leaves hungry.

On Thanksgiving day, I will pick you up (if you do not have a car) and bring you to our house in Acton for a GIANT meal. You will be an honorary member of my weird family for the day. We plan do some mad science, hiking in the trails behind our house (which has been known to devolve into a snow-ball fight) between courses and trivia Bingo with FABULOUS prizes!  As weather permits there may even be a camp-fire. I will drop you back at Olin in the evening.
\subsection{Bartending with Hema}
Alisha Sarang-Sieminski
\\
Starting Bid: \$75
\newline
My wife, Hema, is an excellent amateur bartender. She tends towards herbal infusions and really enjoys crafting a drink (alcoholic and non) for each person's desires. We will host a cocktail party of up to 8 people* in our home with our hodgepodge array of fine bar ware.  Enjoy our company as well as the company of our dog and cat. You provide the liquor, we'll do the mixers and garnishes.

*Must be 21 unless you go totally dry. Also must have a driver.
\subsection{Executive Chef Kris Groth presents a 5 Course Tasting Menu at Chez Somerville}
Mark Somerville
\\
Starting Bid: \$300
\newline
Join us for an evening of high cuisine and high spirits at Chez Somerville.  Olin alums Kris Groth and Mariko Thorbecke, assisted by Olin faculty member Mark Somerville, will serve your party of up to 10  a meal to remember at Mark's house (conveniently located 10 minutes from Olin). 

Just to give you a sense of last year's menu:

Assorted cheeses, chutneys, and nuts, fino sherry

Course 1: Allium 5 ways.  
Course 2: Essex Little neck clams in a spicy chorizo broth, crouton
Course 3: Spicy Thai beef tounge (locally sourced), homemade sweet chili sauce, daikon slaw, lettuce wrap
Course 4: Local Berkshire pork served two ways, served with celery root puree and triticale succotash
Course 5: Butterscotch panna cotta, oatmeal cookie crumbs, crushed meringue, served with birch reduction

Chocolates, port to finish.

For parties of drinking age, appropriate and interesting wines, selected by our excellent sommelier Mariko Thorbecke, accompanied each course.
\subsection{2 AA System Wide Upgrades}
Matthew Hill
\\
Starting Bid: \$100
\newline
I might be an '06er, but I'd like to welcome you to a different kind of "First Class!"

I fly a LOT...like 100,000+ miles a year "lot" and I'm giving 2 coveted System Wide Upgrades on American Airlines to the winner of this auction on the domestic or international flight of your choosing. These go for \$350-450 *each* online, for reference, and 100K of flying earns you just 4 of these each year

Fine Print: 
  - Must be used by the expiration date (2/28/2017)
  - I cannot guarantee availability on your preferred route/date (call AA if you have a date/route in mind and want to check)
  - I will have to call AA and upgrade you after you've booked your flight.
  - No resale allowed (gifting within family/friends is OK)
\subsection{Fresh Handmade Sushi Dinner for 6 in dorms or at my house!}
Michelle Davis
\\
Starting Bid: \$100
\newline
My son has become a sushi master, of sorts. We will find the freshest tuna, hamachi and salmon in town and treat you and your friends to sashimi and rolls. I also make mean fresh spring rolls.
\subsection{Fabulous Brunch/Shopping Outing with Emily and Jessica}
Emily Roper-Doten and Jessica Townsend
\\
Starting Bid: \$50
\newline
Emily Roper-Doten and Jessica Townsend will treat you to a sumptuous brunch and serve as your style mavens for an afternoon of outlet shopping. This is for a group of up to five people - please bid as a group.
\subsection{Epic Handmade Pizza Dinner}
Aaron Hoover
\\
Starting Bid: \$0
\newline
You and 5 others join me at my house for an epic night of pizza making (and eating) accompanied by age-appropriate beverages. Trust me, you have never experienced a pizza bonanza quite like this. I will provide handmade dough, any topping you desire, and dessert by the firepit (weather permitting).  As a bonus, you may receive a sweet nickname from my 3 year-old son. Past favorites have included Doyung "Doe Doe" Lee, Rahil "Rah Phil" Dedhia, and Evan "Kevin" Dorsky.
\subsection{The best meal of your life}
Kimble McCraw '06
\\
Starting Bid: \$100
\newline
This is a gift certificate for dinner for two at The Tasting Counter in Somerville, a 9 course tasting menu. Chef Peter makes magic out of food and food out of magic. He's worked at Aujourd’hui at the Four Seasons, staged at Michelin-starred restaurants, TA'd for Jacques Pepin, and has been working towards this restaurant for more than 20 years. Everything that can be made in house, including things you didn't realize could be made in house (fermenting your own miso?), is made in house. Everything that can be harvested locally is harvested locally (where do you even find local wild flower foragers?). For the curious, the seating all gives a great view of the intricacies involved in preparing fine dining and the  chefs are more than happy to answer questions and explain techniques. But most importantly, the food the delicious and delightful and the whole experience is thought out down to the shape of the counter. You can read more about it in multiple Boston Globe reviews, Boston Magazine's Best of Boston, Eater, and other publications. It will be the best meal you eat this year, if not the best meal of your life.
\subsection{A sweet, professional video}
The Library (Emily + Jeff)
\\
Starting Bid: \$13.37
\newline
Do you want a visual artist statement for your website or portfolio? How about some documentation for your project or a year in review? Perhaps, you'd love a slow motion capture of you or your dog catching a Frisbee and rolling around in mud. We will make you a sweet, professional video on whatever topic you desire. Rules: no more than 3 minutes, limited motion graphics.
\subsection{Boda Borg adventure challenge with profs}
Sam Michalka and Jason Woodard
\\
Starting Bid: \$10
\newline
Sam and Jason will bring 3 people to Boda Borg in Malden, where we will work as a team to solve a series of mental and physical challenges (no need to be an athlete).  High-fiving may occur.
\subsection{Pork King Sweet Italian Sausage}
Glory Hall
\\
Starting Bid: \$8
\newline
Ever had way too much sausage in your freezer? Well I certainly have, and if you want to share in the wonderful experience purchase this frozen 5lb box of the finest Pork King Sweet Italian Sausage money can buy. In stores meat this fine would cost you six bucks, but since this is for charity we want an eight dollar minimum donation to part ways with this sweet sweet Italian sausage.
\subsection{Squat per Dollar}
Bill "o" Wong and David Abrahams
\\
Starting Bid: \$1
\newline
In one workout, Billo and I will squat 200 lbs for a number of reps. The number of reps we will cumulatively do is equal to the number of dollars in the winning bid. We will switch off squatting with as little rest as possible.

At 50 dollars, we will both purchase matching bright pink tank tops and wear them to the gym together.

At 75 dollars, we will livestream the entire workout.

At 100 dollars, Logan Davis will provide commentary over the last 10 minutes of the workout, including post-set and mid-set interviews.

At 200 dollars, every five minutes a timer will go off and whoever is currently squatting must consume a bite-sized candy car mid-set.

At 300 dollars, we might die.

At 400 dollars, we will die.
\subsection{Come fly with me!}
Alexander Scott
\\
Starting Bid: \$30
\newline
Come fly in a small airplane with me! I'll take you up for a couple hours, maybe stop somewhere for lunch, and fly over whatever nearby sights you want to see!
\subsection{OPIUM Show - Minute per Dollar}
OPIUM
\\
Starting Bid: \$10
\newline
OPIUM will perform a show for the whole school with the exact length of the show in minutes equal to the number of dollars in the winning bid.

At 50 dollars, we will perform Bucket of Death as part of the show.
\subsection{Your Face. All the Vehicles.}
Baja, Formula, HPV, OARS
\\
Starting Bid: \$25
\newline
Want to get your face, or the face of your choice*, on not 1, not 2, but 4 Olin team vehicles (Baja, Formula, HPV, and OARS)? If so, this is the item for you! *assuming you've gotten their approval/consent
\subsection{Four Years of Vintage Olin T-Shirts, 2005-2009}
Nikolaus Wittenstein '09
\\
Starting Bid: \$20
\newline
Be the coolest cat in the Oval in your genuine Candidates' Weekend 2008 shirt. 
Be the center of attention with a titillating Sausagefest 2007 shirt (Achtung: Der Sausages ist hüge!).
Impress your SCOPE advisor with SCOPE: Brainwash loud and proud on your torso.
Blend in at Babson with the Babson Players' "You Can't Take It With You"—or stand out with "Beauty and the Beast".

This auction has it all. Nineteen shirts from Olin, five from Babson, and six "miscellaneous". Impress your friends, confuse your professors, try to trick alumni into thinking you were really at Olin with them that whole time.

As a special bonus, the donor will explain to you the historical background of each shirt in the collection, from the "Engineering stress decreases when necking occurs" to the artisanal handmade J-TEAM (one of only five in the world!).

This is a one-of-a-kind collection, comprising every shirt the donor acquired while at Olin, and this is your once-in-a-lifetime chance to be the lucky winner.
\end{document}
