\documentclass[11pt]{article}
\pagestyle{plain} \topmargin -.5in \oddsidemargin 0in
\evensidemargin 0in \textwidth 6.5in \textheight 8in
\setlength{\parindent}{0in}
\begin{document}
\section*{1.3 Pen pals}
Adam Coppola
\\
Starting Bid: \$0
\newline
Number of winners: 2
\newline
Stay in touch over paper letter or email intermittently for the rest of our lives.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{1.4 ninetieswebsite.net for you}
Aidan and Doyung Inc.
\\
Starting Bid: \$0.01
\newline
Number of winners: However many want in
\newline
You provide 3 words, we'll make you a website fit for the 90s.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{1.7 Make Your Google Slides Pretty}
Haley Pelletier
\\
Starting Bid: \$1
\newline
Do you have a presentation coming up? Have you put all the information you want to cover in your slides, only to realize they're ugly and sad? With at least 24 hours advance notice, I will turn your Google Slides into a work of art worthy of the Louvre (or some lesser museum). This does not include any content generation, though I will help you pick out pretty pictures to put in your slides if you so desire. Every \$1 covers 5 slides (which do not all have to be in the same presentation). Email me for examples of past work.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{1.18 Daily Snapcats from Alums}
Alex Crease and Claire Diehl
\\
Starting Bid: \$1
\newline
Number of winners: 2
\newline
Need a little more kitten in your life? Want to be cheered up by endless pictures of a cute cat? Claire and Alex will send you daily Snapcats* of our cat Misty to brighten up your day. At just \$3 per week (rounded up) your day couldnt get any cuter!
*Snapcat: like snapchat, but we send you pictures of cats instead of silly humans
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{1.20 Fantasy Football Advice}
Radmer "Torn ACLs" van der Heyde Chris "RBBCs" Wallace Sawyer "Last Place" Vaughan James "Also last" Jang Griffin "League Champ" Tschurwald and Kevin "Trade Bait" Suzuki
\\
Starting Bid: \$1
\newline
If you have been around this fine group of gentlemen over the past semester you have probably learned one thing: they are playing fantasy football. Well if you too play fantasy football, what better way to prepare for playoffs (or loser's bracket, sorry Sawyer) than receiving the best advice possible. This group knows how to handle ACL tears, suspensions, dry waiver wire, RBBC based teams, you name an issue they have a solution
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{1.22 Walk with Dancer!}
Suite Dreams (3NN)
\\
Starting Bid: \$1
\newline
Number of winners: 1 (small groups accepted)
\newline
Go on a walk with Ashley and Dancer the dog (and probably other super seniors/junior)
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{1.24 A beautiful resume template }
Gabrielle Ewall
\\
Starting Bid: \$1
\newline
I made a very attractive resume template on illustrator. It always garners compliments at career fair. Now it can be yours too!
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{1.26 Be Your Buddy (for a limited amount of time)}
Jen Wei
\\
Starting Bid: \$1
\newline
Need a shop buddy or a running buddy? Want someone to sit with you when you're working late in the AC? Need a quick favor? Just need a buddy? Bid on this, and I can be that person (assuming it fits into my calendar). The higher the bid, the more time I'm willing to put into this.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{1.27 Support You to Gold}
Philip Z Loh
\\
Starting Bid: \$2
\newline
Ever get tilted off the face of the Earth because your Miss Fortune support refuses to buy a Sightstone? Are you salty because you queue support as a secondary role but get it 90\% of the time? I'm a support main and I'll queue with you!
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{1.31 Layup your favorite food}
Dennis Chen, Jennifer Wei, Lucy Wilcox
\\
Starting Bid: \$2.34
\newline
We will layup one (small) perishable dining hall food item of your choice, giving it a nice layer of carbon fiber and epoxy. Here's your chance to get your very own mummified chicken tender.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{1.34 Makeovers!!}
Isabel Blancett \& Lacie Fradet
\\
Starting Bid: \$2.5
\newline
Number of winners: 4
\newline
A makeover done by two Olin students who love to do makeup and hair.  We can do funky makeup for kids or professional/mature makeup for adults.  Each winner gets five touched up (not that you'll need it) pictures with their new look!
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{1.37 Be a star on my youtube channel!}
Shrinidhi Thirumalai
\\
Starting Bid: \$3
\newline
Number of winners: 2
\newline
I have a youtube channel @scrappytreasures, where I teach you how to turn old boring clothes to new fashionable ones. (shirt to bag, shirt to dress, etc.) Guest star in one of my videos! (and maybe even get a free piece of clothing out of it).
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{1.38 The Magic in Your Idea}
Keith Hopper
\\
Starting Bid: \$3
\newline
Ever have an awesome idea, but difficulty describing its awesomeness to others? I can help. I've spoken to a lot of companies and product teams about their ideas, and I love to help find and articulate the genius embedded in all of them.

We'll sit down and talk excitedly about your cool idea - whether its for a road trip, software application, charitable event, pumpkin pie recipe or crazy new business idea. From this, I will write up a brief description of what I think the idea is all about and what makes it great. I can't promise it will be what you intended, but I bet it will be fun.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{1.42 Jet Skiing in the Seattle Area!}
Kelly Brennan
\\
Starting Bid: \$5
\newline
I live in the Seattle Area and i happen to have a jet ski. I love to give people jet ski rides! If you win this item, I will take for an AWESOME jet ski ride when I am home this summer!* 

If bidding goes above \$15, I'll let you drive. If bidding goes above \$25, I'll let you drive by yourself! 

Note: You are welcome to go in with someone else on this item, because the jet ski can hold 3 people total!
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{1.46 Cover Letter}
Sally Phelps
\\
Starting Bid: \$5
\newline
You no longer need to be INTIMIDATED by that cover letter that you've been dreading working on.  Sally will write a killer cover letter for you that will get you the job or internship of your dreams!
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{1.49 A Terrible CAD of Your Choice}
Josh Sapers
\\
Starting Bid: \$5
\newline
I will draw you anything you want, but there is a a small caveat: it will be terrible. It will look like the part you want, but there will be blue lines aplenty, equations that make no sense, and plenty of superfluous steps (many counter productive). For every \$5, I will spend 1 hour on the cad. if it hits \$25 I will use both Solidworks and Onshape and transfer between the two.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{1.50 Resume or essay editing}
Ilana Walder-Biesanz
\\
Starting Bid: \$10
\newline
I'm a former Olin writing tutor, and I also worked part-time as a resume and essay editor for a college admissions coaching service for five years. I will provide detailed feedback on an essay or resume (and in the case of resumes, can also do re-formatting). Maximum two-page resume or four-page essay. Add an essay page or cover letter for every \$5 above the \$10 starting bid. NB: I am most experienced with fellowship applications and college and grad school admissions essays.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{1.51 Your Name (Or Anything) in a Nationally-Published Puzzle}
Philip Z Loh
\\
Starting Bid: \$10
\newline
I write for many puzzle events that run nationally. Do you want to sneak your name into one? Your crush's name? The word "penguin"? I'll find the most appropriate way to get you your next brush with fame.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{1.53 Talk to you about grad school and/or help you apply!}
Jeff Holzgrafe and Brendan Quinlivan
\\
Starting Bid: \$10
\newline
Do you wonder why engineering grad programs make you write some long essay? Are you yearning for the American (or British) tax payer to fund your education??? Let us give you a hand!
 
NSF GRFP? NDSEG? Goldwater? Marshall? you name a fellowship or grad school you want to apply to we can help you out! We can also talk you through REU applications, grad school visits, chat about the application process, or help you think about your future life in grad school. We’ll give you an hour of our eyeballs for every \$10 you spend!
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{1.54 Free lodging in Edmonton, Alberta}
Beth Sterling Lee ('08) and Michael Lee
\\
Starting Bid: \$10
\newline
You never know what might bring you awfully close to the icy end of the Earth. Be prepared by ensuring you have lodging (for up to three nights)!  We have a spare bedroom and private bathroom in our basement available for anyone willing to brace Tim Horton's "coffee" and -40 temperatures in the winter. I'm happy to show you the famous-ish West Edmonton Mall, various cafes that serve awesome coffee, and how to vent your spleen in Quebec French. My infamous desserts plus ridiculous amounts of affection from two cats and a dog are complimentary.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{1.58 How to Write a News Release }
Joe Hunter
\\
Starting Bid: \$15
\newline
A short but pithy lesson on how to write a news release
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{1.59 So You Wanna Work in Video Games...}
Brian Shih
\\
Starting Bid: \$15
\newline
I’ve been working at a mobile gaming company as a PM for 5 years and was a PM at Google before that. I can talk to you about what it’s like making games, game design theory, games to play and product management that’s specific to making games. If you love playing games and have ever wondered about working in games, I would love to talk to you.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{1.60 Career Coaching Session}
Lindsay Gordon ('07)
\\
Starting Bid: \$20
\newline
Number of winners: 5
\newline
Feeling overworked, underutilized or undervalued at your job? Looking for ways to make a change so you don't dread going to work every day? I'm a career coach and my main focus is helping people gain a lot of self-awareness so that they can make career choices based on what they know about themselves. I love working with analytically minded people who love learning and are looking for a really practical and structured way to get to know themselves. Each winner will get a 60 minute coaching session with me where we'll assess your level of fulfillment in 8 different areas of your current role and create a plan of action to make some changes (\$150 value, www.alifeofoptions.com for more info)
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{1.61 Resume}
Sally Phelps
\\
Starting Bid: \$20
\newline

Sally will turn your skills and experiences into a fantastic resume that is SURE to get you an interview!
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{1.63 Facebook Advertising Advice + Credit}
Chris Marra
\\
Starting Bid: \$50
\newline
Number of winners: 1-4
\newline
Do the terms Custom Audience, Pixel Conversion, Lookalikes, Targeting, and Outcomes confuse you? Have you always wanted to advertise your business or service on Facebook? I will coach you through how Facebook's ads platform works, the different options you have on ad format display, targeting, measurement, and the types of actions you can try to drive. Each winner will also work with me to run \$250 worth of ads using credits provided by me. We'll probably do this as 2-3 working sessions as a group, either at Facebook HQ or over VC. The top 4 bids will be chosen, and you may bid multiple times if you want a higher budget for your ads :-).
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{2.1 Whisky Tasting}
Chris Wallace, Nagy Hakim, Luke Morris
\\
Starting Bid: \$0
\newline
Number of winners: 2
\newline
Chris, Nagy, and Luke will pull out some of their favorite whisky for a generous sampling session with YOU. We'll discuss why we love whisky, what we like and dislike about our various options, and life and its meaning.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{2.3 Gluten-free Vegan Zucchini\^Pumpkin Bread Recipe}
Katie (Rivard) Mazaitis
\\
Starting Bid: \$1
\newline
I spent the summer developing a reliable, tender, fluffy, not-crumbly recipe for zucchini bread that is both gluten-free and vegan. This is not a drill. There were 8 different prototypes. It also works with pumpkin. I will send you the recipe as well as my dev notes. If bidding goes over \$10, I'll also send you an ingredient kit.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{2.5 Truffles, for a day or a lifetime}
Rachel Boy
\\
Starting Bid: \$1
\newline
"Give a person truffles, and they will be able to make friends for a day or two. Teach a person to make truffles, and they will be able to make friends for the rest of their lives."
- Traditional proverb

With this item, you get:
1) Truffles! Every ten dollars gets you fifteen truffles. We'll work together on flavors, and I'll ship them to you*. (In the past, my truffles have been used for parties, weddings, Christmas presents, and eating them all yourself.)

2) Your choice of:
    a) Detailed recipes for the truffles flavors I've made for you, along with written up notes on truffle-making techniques, some of the chemistry involved, and suggestions for recipe modifications.

    b) A Skype session**, no longer than one hour, where I tell you how I made the truffles I sent you, give you advice on truffle-making in general, dive into some of the relevant science, and generally answer your questions about life (i.e. chocolate making).

*I will only ship truffles during the cool months - no summer truffles unless you can make it to Seattle to get them from me.
**The tutorial can also be in-person, should you be able to make it Seattle.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{2.11 We'll bake the world's best brownies }
Mackenzie Frackleton
\\
Starting Bid: \$3
\newline
3 layers: cookie dough, oreos, and brownie batter. The more you donate, the better these will be ( it's could all be made from scratch/double stuffed)
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{2.16 Dessert version of you!}
Chloe Grubb
\\
Starting Bid: \$5
\newline
I will create you a dessert that encompasses you, as a person, to the best of my abilities. We can have  discussion where you tell me about yourself and then I'll make you some tasty baked treat based off what I learn!
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{2.22 Hipster Coffee}
Morgan Bassford
\\
Starting Bid: \$5
\newline
I live in the Pacific Northwest, land of rain, flannel, man buns, "Coexist" bumper stickers and, of course, coffee. I will find (and mail) you the most hipster of the hipster coffee I can find from either Portland or Seattle. You've never heard of it, guaranteed! If you win, please specify what kind of roast you prefer as well your desired flavor profile (i.e. "lightly floral with undertones of existential dread").
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{2.25 Sweet Basil Pesto}
Jen Wei
\\
Starting Bid: \$5
\newline
I've heard rumors that the pesto at Sweet Basil is quite delicious. If you win, I'll get you a pint of it (if you're outside of the Boston area, you'll have to figure out/cover shipping).
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{2.26 Really Good Food, and Pick-Your-Own Good Company}
Jared, Charlie, Ian, and Lauren
\\
Starting Bid: \$5
\newline
Come to Yume Wo Katare (Dream Ramen), a wonderful ramen place in Camberville, with your choice of any two out of the four of: Jared, Charlie, Ian, and Lauren. We won't get our feelings hurt, we promise. We just want to share the beauty of this restaurant with you. 

Notes: Bids with a multitude of people probably won't work out, because it's best to experience this restaurant with three, unless one of you wants to come with two of us and the other wants to make a separate trip with the other two (which would also be great). More than \$13 (per person bid) and we'll cover your meal! Not recommended for vegetarians/vegans/those who don't eat pork. Open to anyone, whether you know us or not! :3
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{2.27 Which honey from Holliston MA is better?}
Sharon Woodward
\\
Starting Bid: \$5
\newline
2 jars of honey
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{2.28 ra(nt)men}
Brandon Chiou
\\
Starting Bid: \$9.98
\newline
You have pent-up frustrations about classes/work/people/etc. I have the know on the best ramen places in Boston. I'll treat you to a bowl of ramen and listen to your troubles. I'll even offer some mediocre advice, but at least you'll have ramen.

And elevated blood pressure.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{2.32 A Lovely Cake, Part II}
Claire Beery
\\
Starting Bid: \$10
\newline
I will make you a lovely cake. I make very yummy cakes. They look nice too. Design inspired by requester preferences. To me delivered anywhere on campus on date of winner's choice. Can only make use of this prize during Spring Term 2017. Minimum bid = 2 x 6" round. Increased bids results in larger fancier cakes. Alternatively, high bids (\$30+) can request demonstrative lessons as I bake/make the cake and decorations.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{2.33 Ice Cream (your choice of flavor)}
Shane Skikne
\\
Starting Bid: \$10
\newline
I love ice cream. Feeding that addiction I have found is easier with my own ice cream maker. Win this item and I will make you about 1 quart of the ice cream of your choice. Choose a well-known flavor or make one up. I'll figure out how to make it (If you choose something like cheddar ice cream, I make no guarantees about the quality of the ice cream). If this goes above \$40, I'll make you ~3 quarts. If this goes above \$60, I'll make 1-1.5 quarts of ice cream with you (and bring you a quart pre-made)! I bring the ingredients and machine, you bring yourself and we make ice cream! This can be redeemed in the greater Boston area (before 12/5) or Bay Area (after 12/5). My favorite ice creams so far: Blueberry Cheesecake Ice Cream, Cocoa Coffee Ice Cream, Vegan Coconut Banana Ice Cream.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{2.34 Homemade Banana Chip Bread}
Harold Jaffe
\\
Starting Bid: \$10
\newline
A big ol' loaf of deliciousness! And since it has bananas in it, it's healthy* for you. If you win this item, I will bake a loaf of banana bread with whatever mix-ins you like--chocolate chips, nuts, even raisins--and mail it wherever you want!

*Actual salubrity may vary.
**If you are allergic to bananas I will try my best to find an equally delectable substitution.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{2.38 Take you to a very nice local Asian food place (maybe hotpot? maybe dim sum maybe else?)}
Zhecan Wang
\\
Starting Bid: \$10
\newline
Number of winners: 5
\newline
Take you to an authenticate local asian food place
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{2.40 w(h)ine}
Brandon Chiou
\\
Starting Bid: \$14.99
\newline
Some wines pair nicely with certain foods, but there's only one thing that pairs with all wines - a whole lotta smack. We'll hang out at my apartment and you can complain to me over some wine. Groups ok.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{2.42 Honey from Parcel Bees, the Olin honey CSA}
Sustainable Beekeeping co-curricular students
\\
Starting Bid: \$15
\newline
Number of winners: 4
\newline
1/2 pint of Olin honey
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{2.45 Delicious Toffee Brittle}
Ari Chae '15
\\
Starting Bid: \$20
\newline
There's a stand in the Ferry Building in San Francisco called GL Alfieri (look it up!) that sells delicious flavors of toffee brittle (sea salt, coffee, w/ various nuts, etc). It is INCREDIBLY addictive. Bid on this item and I'll send you some! If you bid high, I'll send you a lot. Trust me, it's amazing.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{2.47 3 Course Meal for 8}
Rebecca's Cafe
\\
Starting Bid: \$50
\newline
Chef Kevin will prepare a scratch made meal for you and 7 of your friends, to be served in the dining hall. You will plan the menu with Kevin by picking a theme and he will execute it. You will be served 3 courses by the Jim Drumheller while Chef Kevin describes each course to you. A similar catering meal at full cost would be around \$120 per person.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{3.3 SAC event in your honor}
Student Activities Committee (SAC)
\\
Starting Bid: \$1
\newline
Number of winners: Any \#
\newline
SAC will throw an event in your honor! If you bid:
\$25 - You get to choose the event
\$60 - It'll be themed around you (e.g., we'll put your face everywhere)
\$150 - We'll make it a SAC tradition and do it again next year
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{3.4 Laur \& Charl in the Morning! Now featuring... you!}
Lauren Gulland, Charlie Weiss
\\
Starting Bid: \$1
\newline
If you've ever seen Community, you're familiar with Troy and Abed (if not, tinyurl.com/laurncharl). Well now, we bring you Laur \& Charl in the Morning. Be featured on the premiere illegitimate live TV show at Olin! No TVs, or cameras for that matter, will be involved. Basically, be dumb with us.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{3.5 Murder Mystery Party Entry}
Claire Beery
\\
Starting Bid: \$2
\newline
Join my comrades and I for a night of love turned murder this Valentines Day. Food and Drink provided. No door fee for winning bid.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{3.6 Afternoon with cats!}
Tiana Veldwisch '08
\\
Starting Bid: \$3
\newline
Do you love cats but not have your own cats to play with? I have THREE fantastic, playful, adorable cats in a variety of shapes and colors! You can come spend an afternoon playing with these cats! They may do tricks for treats, they will chase things, they may eventually sit in your lap, but they're cats, they do what they want. They don't travel, so you have to come to us (Davis Sq area, Somerville), at some mutually-agreeable time. I'll make some tea/cocoa and snacks.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{3.11 Surprise Adventure with Team Insulet!}
The Insulet SCOPE Team (Bonnie Ishiguro, Meg McCauley, Charlie Mouton, Haley Pelletier, Meghan Tighe)
\\
Starting Bid: \$5
\newline
The Insulet SCOPE Team, aka the coolest people you've ever met, will take YOU and your friends on a surprise adventure of our choosing. We'll also let you meet our team mascot, Tim, and take a SCOPE selfie with you! Limit 5 people.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{3.12 Holland House Homemade Meal}
Eric Schneider
\\
Starting Bid: \$5
\newline
We the denizens* of 206 Holland St in glorious Somerville welcome you to the Grand Holland House Hotel** for a sumptuous homemade feast***. Limousine delivery services**** provided to and from your residence***** if you need it! We usually do dinners on Wednesday and brunches on Saturday, but if you win and neither of those work we can probably figure something out :)

Incentives:
-- Every \$10 is an extra person, up to 8 people
-- At \$30 you can help choose the food
-- At \$60 we will decorate the house according to a theme of your choosing
-- At \$80 it's your birthday! No really, it is, we swear. You'll think it is, anyway :)
-- At \$100 we'll all wear onesies and provide one for the birthday person

* - Misty (cat, cuddleable) Nicole Rifkin (winners get her undying affection), Alex Crease, Claire Diehl, Amanda Sutherland, Victoria Coleman, Eric Schneider, Dan Huber. Mostly Olin alums
** - well, it's a house anyway
*** - there will almost certainly be food, and it won't be Dining Hall food! Admit it, that's all you really want
**** - transportation in some car
***** - assuming you live in the Boston area to some approximation
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{3.14 Lake Waban walk and meal}
Alison Black
\\
Starting Bid: \$10
\newline
Let's take a walk around Lake Waban in Wellesley followed by a meal in Wellesley.  Walking around the lake is beautiful during any season of the year, so we just need to find a mutually agreeable time.  You can bring a friend too!
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{3.15 dinner at Sara's house}
Sara Hendren
\\
Starting Bid: \$10
\newline
Number of winners: 4
\newline
The four winners of this item get a group invitation to Sara's house in Cambridge for dinner, likely on a late Sunday afternoon/evening. My family and I will cook; all dietary preferences are easy to accommodate. (You just have to like little kids.)
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{3.16 Cinderella (or other) Tix + Backstage Tour}
Brian Liebson
\\
Starting Bid: \$10
\newline
As of right now (Nov. 2, 2016) I am in the national tour of Rodgers and Hammerstein's Cinderella the Musical. Theoretically, I will be in this show at least until June 22, 2017. If you buy this, I'll give you 2 free tickets to the show at whatever date/location you desire and a complimentary backstage tour led by yours truly. If, by the time you redeem this, I am in a different show, I'll do the same for whatever show that is. You can check out dates/locations of the tour at http://www.cinderellaonbroadway.com/tour/.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{3.20 2 Red Sox Tickets }
Sharon Woodward
\\
Starting Bid: \$25
\newline
Choose from 3 dates (TBD in late March) to see the Red Sox in 2017!  Grandstand Section 8, Row 3, aisle seats.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{3.21 Climbing Adventure}
Ben Smith '13
\\
Starting Bid: \$25
\newline
I'll take you (and one friend, if you wish) on an unforgettable climbing adventure. It can be a rock, a frozen waterfall, or a mountain. Location, objective, and number of days are all negotiable. 

Never climbed a mountain (or even the stairs to the AC's 4th floor)? No worries. I'll help you pick an objective that is appropriate for you.

I work as a rock climbing guide on the weekends. As of 1/1/17, I'll be an unemployed climbing bum. This means I'll have plenty of time to take you on an adventure.

Potential objectives to wet your whistle:
- Mt. Baker, WA
- Solar Slab, Red Rock Canyon, NV
- Cathedral Peak, Yosemite Nat'l Park, CA

Logistics:
Location: I'll be traveling across the western US in 2017. I will not fly to meet you for our objective, as I'll be unemployed. However, with planning and the right objective, I can meet you there.
Gear: You may need to rent a few things depending on the objective. I have most gear.
Travel: You will be responsible for financing your travel.
Lodging: I've got a rad windowless van that you can sleep in for free, and I'll sleep in a tent on the ground (The van actually is pretty rad). All other arrangements are on you.

Disclaimer: I am not a certified guide through the American Mountain Guide Association.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{3.22 Tour of Jet Propulsion Lab/NASA}
Blair Emanuel
\\
Starting Bid: \$25
\newline
Number of winners: 2
\newline
What it sounds like - a two-hour tour of the Jet Propulsion Laboratory in Pasadena, CA for 5 people. Highlights include Mission Control, the Spacecraft Assembly Facility, and the Mars Yard. I'll also show you some of the stuff I'm currently working on. The tour requires at least one month advance notice of all participants (so they can be cleared to come on lab) and is unfortunately only for US citizens (sorry, but foreign nationals are harder to get clearance for). This item will expire on 12/31/2017.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{3.23 Beverage Tasting!}
Brandon Chiou, Carly Ingrao, Mariko Thorbecke, Kris Groth
\\
Starting Bid: \$40
\newline
The founders of Olin's only chartered fine wine/craft beverages tasting club (+ Kris) are back! Gather some of your friend(s) and get \#learnt with a custom flight of a beverage type of your choosing. Accoutrements provided.

Max group of 4.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{4.1 Practice Software Interview}
Andy Getz '10
\\
Starting Bid: \$0.99
\newline
Number of winners: 2
\newline
I have interviewed more than 50 candidates for software engineering roles at Google.  I will come to Olin and interview you in much the same fashion, and then I will provide feedback, suggestions, and assessment.

I can do intern and full-time interviews.  I can deal with whatever programming language you prefer to use, but my feedback will be best if you pick one I know well: C, C++, Python, Go.  One interview covers one or two problems (with many sub-parts) and takes about an hour.

I did a group version of this as part of a Google information session on 10/17.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{4.2 Knots Lesson}
Rebecca J
\\
Starting Bid: \$1
\newline
I'll teach you knots! Whether you can barely tie your shoes or can tie a zeppelin bend behind your back, I'll introduce you to a few new useful, interesting, and fun knots, and either instruct or learn along with you until you've got them down solid.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{4.4 Enlightenment}
Graham Hooton
\\
Starting Bid: \$1
\newline
Are you engaged in the pursuit of wisdom? Do you examine the nature of your thoughts, habits, and beliefs? Let's share our observations with one another by messages and/or skype calls for the next three months!
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{4.5 go thrifting with us}
Izzy, Hannah, Kristyn(maybe)
\\
Starting Bid: \$1
\newline
We will take you  and a friend thrifting and teach you how to spot them good dealz and get dat hipster grandma style
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{4.12 Become a Ninja}
Anne LoVerso
\\
Starting Bid: \$2
\newline
I will take you with me to my American Ninja Warrior class (Fridays 5-6pm) and pay your way.  Together, we will learn how to be ninjas.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{4.14 Grass Mowing and Kite Flying Lessons}
Andrew Pan and Jonah Spear
\\
Starting Bid: \$2.1
\newline
With a combined 15 years of yard maintenance and kite soaring experience, we will teach you the tips and tricks of the trade.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{4.19 Climbing Coaching!}
Katya Soltan
\\
Starting Bid: \$20
\newline
I can coach you in climbing - technique, training, and support. I have a free guest pass per month, and can take you to the gym for a day of your choosing. If you've never climbed before, we'll start from the beginning! If you have, I can give you pointers =) I will belay you until you cannot climb anymore, if you so choose.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{4.20 Teach you to jewelry}
Claire Kincaid
\\
Starting Bid: \$30
\newline
I will teach you to make the jewelries.  The more you bid the more complicated the techniques that you will eventually learn, but we'll start small.  I can teach just about anything on a basic level and am happy to learn advanced techniques alongside you if you want to explore something that I've not done before
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{5.2 Postcard}
Forrest
\\
Starting Bid: \$0.1
\newline
Number of winners: 3
\newline
I'll send you a cyanotype postcard from where I am (probably home). If I know you, I'll write something personal on it, if not, whatever. If you have opinions on subject matter, let me know, or it'll just be a picture of my face. It might be a picture of my face regardless. Make sure to send me your address if you win, so I can actually send it to you. Up to 3 people can win, though I don't know why that many people would bid on this.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{5.3 Custom Friendship Bracelet}
Rebecca J
\\
Starting Bid: \$0.5
\newline
A colorful knotted embroidery thread bracelet with whatever pattern you'd like! The higher the bid, the wider the bracelet and the more colors you can choose from. I can do words, pictures, eye-popping patterns and more, and I'm happy to help you find or design a great-looking design.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{5.4 Knit you a tiny thing}
Amanda Sutherland
\\
Starting Bid: \$0.5
\newline
Number of winners: eh? Just please done have me doing this until I'm an old granny. 
\newline
I love tiny things. They're stupidly adorable. Who doesn't love tiny things? I will knit you a tiny thing with toothpicks (really, have done before) and it will be your new tiny friend. Take it in your pocket to class, or whatever floats your boat. 

I can probably make any creature you want, but definitely are tiny owls, chickens, pirates (still not kidding), dogs, computers, hot dogs, foxes, ... you get the idea. 

If you go beyond 4, I will make another one. Every multiple of four gets you another one until 24, at which point I'll knit you a larger cute thing too. After that, who knows...
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{5.6 The Most Seattle Rain Boots}
Rachel Boy and Maddie Perry
\\
Starting Bid: \$1
\newline
Seattle - the home of grunge, the space needle, hipster coffee shops, and rain. After surviving a Seattle "winter", we know two things are crucial to functioning in any level of wetness: 1) rain boots, and 2) a nonchalant attitude about getting damp. We can't give you the second, but we can give you a pair of rain boots, decorated in our own inimitable style to reflect the values of the Pacific Northwest. And who knows - maybe with such stylish boots to wear, you'll be more excited about the rain!

*You can make whatever requests you want about the boots. We'll try to get boots of the right size, and we'll perhaps let you guide our artistic vision, but ultimately we answer only to the muse of Seattle for our creation.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{5.8 Dinosaur Art IV: Rebirth of the Return of the Revenge of the Dinosaurs!}
Harold Jaffe
\\
Starting Bid: \$1
\newline
Add an extra touch of class to any room with a tasteful and elegant picture of a dinosaur! If you win this item, I will draw for you a picture of the dinosaur of your choosing, in your choice of black-and-white or color, and your choice of pencil, marker, or crayon. (If you choose black-and-white and crayon, I might think you are a bit silly.)

*I use the word ”dinosaur” in the vernacular sense, including such prehistoric animals as ”mosasaurs, ichthyosaurs, pterosaurs, plesiosaurs, and Dimetrodon.” \textless https://en.wikipedia.org/wiki/Dinosaur\textgreater
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{5.9 Cute animal drawing}
Halley Pollock-Muskin
\\
Starting Bid: \$1
\newline
I will make you a poorly drawn cute animal picture. You choose the animal.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{5.10 Shitty Poster!}
Keenan \& Aaron
\\
Starting Bid: \$2
\newline
We will sincerely try to make a shitty, shitty poster for you. Trust us, we know how to make things shitty. Like reeeaaal shitty. Can be used for an event, your room, or the room of your enemy!
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{5.11 GoodRobit Robit}
GoodRobit (Shane Skikne, Alex Crease, and Isaac Vandor)
\\
Starting Bid: \$2
\newline
Win this item and we will make you your very own GoodRobit Robit! It'll be one of a kind! 
How it works: You give us a task and we will build you a robot that has nothing to do with that task (for no one's  definition of robot). 
Our level of effort will relate to your donation according to the following formula: Effort = (Winning Bid Price / 7) to the power of the number letters in the first 2 letters of your name
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{5.12 Crocheted Mathematical Shape}
Ariana Olson
\\
Starting Bid: \$2
\newline
I will crochet a mathematical shape for the highest bidder in their choice of yarn color. The shape will be proportional in complexity to the size of the highest bid. For bids under \$15, I'll make you some kind of hyperbolic function. For higher bids I will make you  a Klein bottle (which doubles as a pretty cool hat, just in time for winter!)
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{5.13 I'll Make You Something DOPEE}
Charlie Mouton
\\
Starting Bid: \$3
\newline
I will make you something awesome. The more you bid, the more say you can have on what I make for you. My skills include screen printing, laser cutting, shopbotting, visual design, etc.

Depending on the job, I will cover supplies.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{5.14 A Print of one's of my digital photo of your choosing}
Charlie Mouton
\\
Starting Bid: \$3
\newline
I have taken some pretty cool photos over my time at Olin. I will print (and frame, if the bid is \textgreater \$20) an image of your choosing that I have shot.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{5.16 Cozy Afghan for each top two bidders}
Molly Tomeny
\\
Starting Bid: \$5
\newline
Number of winners: 2
\newline
I will give you each a hand-made crochet afghan, approx 40"x60". Top two bidders each win one afghan. Machine washable, tumble dry.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{5.17 A beautiful letter, for you or to you}
Ilana Walder-Biesanz
\\
Starting Bid: \$5
\newline
I will write a letter, to you or on your behalf. (I can decide on the exact contents, in which case I will strictly follow correspondence etiquette, or I can write out the message of your choice.) It will be in beautiful cursive, written with a fountain pen on correctly sized 100\% cotton paper from Crane's \& Co. I will seal it with sealing wax (optional).
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{5.18 Iridescent Blue and Silver Necklace}
Ruth Hunter
\\
Starting Bid: \$5
\newline
Textured silver beads, stamped with a crescent design reminiscent of the Olin Oval, are paired with 1/2" round agate stones, whose iridescent blue surfaces are pocked with irregular geode fissures. Necklace is 16-inches long and comes with matching earrings on sterling silver earwires.  Necklace terminates with jump-rings, so you can easily swap the simple magnetic clasp out if you prefer a different style.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{5.19 Custom Glass Bead}
Jiaying Wei
\\
Starting Bid: \$5
\newline
Number of winners: 2
\newline
I'll work with you to create a custom flame worked bead of your design which can be made into a necklace, bracelet, etc.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{5.20 Logo of Your Face}
Keenan
\\
Starting Bid: \$5
\newline
I'll make an icon of your face! Maybe I'll let you decide which photo, and maybe not. I guess it depends on how much is donated.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{5.22 Make you a Snapchat Geofilter}
Aaron Greiner
\\
Starting Bid: \$5
\newline
I will make you a Snapchat Geofilter, and submit it to be live. You can choose what the Geofilter is for and the location. No guarantee on whether it will be accepted or not, but ill do my best.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{5.24 Itty Bitty Shitty Knitty}
Lauren Gulland, Charlie Weiss
\\
Starting Bid: \$5
\newline
We will skillfully co-knit you something shitty. It'll be great though, trust us. We're professionals.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{5.25 Custom Pottery}
Lydia Zuehsow
\\
Starting Bid: \$10
\newline
Number of winners: 3
\newline
For the top three bidders, I will throw and glaze any pottery object of your choosing (that is smaller than a dodge ball). Bowls, plates, cups, teapots, planters, sculptures, you name it.
(I reserve the right to refuse NSFW sculptures/objects.)
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{5.26 Calligraphy Snail Mail}
Lindsay Gordon ('07)
\\
Starting Bid: \$10
\newline
I love calligraphy and I'm always looking for more excuses to practice. I’ll send you 3 cards with beautifully written/decorated envelopes and I can also do special request calligraphy projects if there's something specific you want!
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{5.27 Handcrafted cards with my photography}
Lindsay Gordon ('07)
\\
Starting Bid: \$10
\newline
I love photography and enjoy printing out my photos, making them into cards and giving them to friends and family as gifts. I’d like to let you choose ten of my photos, I’ll print them out and mount them on cards for you and you can treat your friends and family to some handmade snail mail. Check out some example photos at lindsaygordon.com/photography
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{5.28 Your own personal mug of}
Mark Somerville
\\
Starting Bid: \$10
\newline
Number of winners: 6
\newline
Tired of stealing mugs from the acronym? Jealous of all the "cool kids" who have real, handmade ceramic mugs?  This is your chance to rectify the situation. I will make custom mugs for the top 6 bidders on this item.  Bids exceeding \$30 can request custom pieces (e.g., large serving bowls); bids exceeding \$50 can request 3-4 piece sets (e.g., teapot + 2 cups, 4 cereal bowls, etc).  Note that there will be some delay in the creation of your pieces, as Mark's wrist is currently broken.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{5.29 Draw you a Picture}
Tehya Stockman
\\
Starting Bid: \$10
\newline
I will draw something of your choice in either pen or on scratch board. I have drawn things for commission and as gifts  and specialize in realistic, detailed renderings. Here's a portfolio of some of the things I've drawn: http://scjspitz.wixsite.com/tehyamarie/drawings.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{5.31 Portable Hug}
Tatiana Anthony
\\
Starting Bid: \$15
\newline
A 6 foot long flannel tube filled with rice that is great for when you really just need a hug or cuddle. You get to pick the colour.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{5.33 GoodRobit Shirts}
GoodRobit (Repped by Shane Skikne, Alex Crease, and Isaac Vandor)
\\
Starting Bid: \$20
\newline
Number of winners: No limit.
\newline
Have you ever wanted to be the coolest kid in school! Now you can with your very own limited edition, GoodRobit shirt. Don't know what GoodRobit is? Well, we're only the second fastest growing robotics company in Western Needham (Needham HS Robotics is tough to beat).

The details: If at least 10 shirts are wanted, we'll design and order goodrobit shirts from chillybear (they'll be nice, comfy shirts). Each shirts costs \$20 and everything over cost goes to the SERV Auction.  Put down your name and the dollars you're willing to put in (1 shirt for each \$20 entered). Everyone who bids on this pays and you don't need to beat other bids.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{5.35 Mermaid Tail Blanket by Crocheted by Krystal Monique}
Krystal Burgos
\\
Starting Bid: \$25
\newline
Keep your feet and legs warm while fulfilling your dreams of being a mermaid with  a soft and cozy crocheted mermaid tail blanket!
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{5.36 Cosplay help}
Lydia Zuehsow
\\
Starting Bid: \$25
\newline
I will construct one item/accessory of your choosing for a cosplay or costume, as accurately as I can make it. All the professionalism, none of the headache.
Item must be smaller than a microwave.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{5.37 Make you a jewelry thing}
Claire Kincaid
\\
Starting Bid: \$30
\newline
Number of winners: 1 or as many people as split the winning entry.
\newline
I will make you a custom piece of jewelry!  the higher the bid goes the more expensive your piece will be-- this includes precious metals and stones. You can have a say in the design or you can leave it entirely up to me.  Minimum bid will get you a copper or nickel bracelet or earrings.  Materials can range up to sterling silver and precious stones.  I can cut the stones myself, or I can buy them.  Techniques are unlimited (casting, wire, sheet metal forming) seriously, go for it.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{5.38 Custom embroidery on something of yours}
Lilia Chan
\\
Starting Bid: \$50
\newline
I am doing an OSS in Chinese silk embroidery and it has been very fun, but painstaking work, which has made me appreciate this art form. I will embroider a custom design (of your choice, but it really can't be extraordinary complex) on a personal item of yours (shirt, bag, handkerchief) out of cotton thread. If it applies I will try to use the same techniques in Chinese embroidery on your piece. If you would like to see what it might look like, just shoot me an email and I'll show you what I'm working on.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{5.39 Sculpt you a thing with wire}
Claire Kincaid
\\
Starting Bid: \$150
\newline
Number of winners: 1 or whoever splits the winning bid.  I can work with a team of winners if need be-- if they all want small, simple sculptures can do, if they want to share one large ridiculously complicated sculpture can do, it depends on how much they pay
\newline
I will sculpt you a thing out of rebar tie! examples include my wire dragon sculpture and my mask from halloween!  I love this method of sculpture and I will gladly make you a thing for charity.  It can be a random thing or something that you design yourself! The more money this item gets, the more extravagant the sculpture will be!
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{6.3 Your Beautiful Face on Mk.2}
Olin Electric Motorsports
\\
Starting Bid: \$0
\newline
We'll put a face of your choosing on the body panels of Mk.2, this year's Formula SAE Electric Vehicle.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{6.6 A sad feeling}
Justin Kunimune
\\
Starting Bid: \$0.01
\newline
Aww.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{6.7 Lauren Gulland}
Linnea Laux
\\
Starting Bid: \$0.01
\newline
You know who she is.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{6.8 A Penny}
Lydia Zuehsow
\\
Starting Bid: \$0.01
\newline
An ordinary penny. Who even uses these anymore?
Give this (obsolete) penny some love and make it feel extra special! \textless 3
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{6.11 Daily Mitchchat}
Mitch Cieminski
\\
Starting Bid: \$1
\newline
Number of winners: 5
\newline
Do you like snapchat? Do you like mitch? What if you could get a daily dose of mitch on snapchat? Well now you can! The top three winners of this item will get a snapchat from mitch every day for at least one year. You could see mitch's great journey after graduation unfold! See the life of mitch as only his front-facing camera can. With Mitchchat.

If the bidding gets to \$20. I'll also sing in the snapchats on occasion
If the bidding gets to \$35, I'll make a point to do at least one interesting thing a week, and snapchat you that thing
If the bidding gets to \$50, I'll send the top winner a private, just-for-them snapchat every day
If the bidding gets to \$70 I'll send EVERY winner a private, just-for-them snapchat every day AND I'll snapchat them back if they reply
If the bidding gets to \$90, I'll sing in every other snapchat
If the bidding gets to \$91, I'll sing in every /other/ snapchat, for a total of every snapchat
If the bidding gets to \$92, I won't sing in any snapchats
If the bidding gets to \$100, I'll do something awesome and I'm not sure what. It'll be related to snapchats though
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{6.12 \$20 Boost}
Byron Wasti
\\
Starting Bid: \$1
\newline
I will add \$20 to any of your bids.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{6.13 One of my sweaters}
Linnea Laux
\\
Starting Bid: \$1
\newline
If you've seen me around in colder weather, you may have noticed that I have an amazing sweater collection. Sadly, I cannot justify owning so many beautiful bulky sweaters with my current lifestyle. Winning this item will allow you to become the owner of one of three diverse sweaters with lots of character and warmth, each of which has its own story (2 of 3 are handmade). The sweaters will fit people my height (5'10") and smaller for the most part, though one is pretty big. Sweater viewing and trying on available upon request.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{6.14 A Thing from Switzerland}
Erika Tsutsumi
\\
Starting Bid: \$1
\newline
I'll be in Switzerland in November, and I will try to find an item for you that costs exactly the same as the winning bid. (Assuming the swiss franc to be equal to the dollar, the real exchange rate right now is 1.01 CHF/USD but who cares.)

It'll be cool. 

Limit \$50 USD. I mean, I suppose you can bid \textgreater \$50 but I might change the reward if you do.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{6.16 Dope mixtape}
Kai Levy
\\
Starting Bid: \$1
\newline
I'll make a mixtape for you that is personally tailored to your tastes with an emphasis on discovering new artists. It'll be sweet.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{6.17 Weird Emails}
Sssssssssssssssssssss
\\
Starting Bid: \$1
\newline
Some weird alumni people will write you some number of weird emails at some level of weirdness probably proportional to something.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{6.18 Care Package from Estonia}
Victoria Preston
\\
Starting Bid: \$1
\newline
Estonia (that's south of Finland and east of Russia) has a unique culture, which you will be treated to with this care package! Items may include: chocolates, traditional snacks, handmade warm things, and so forth! If you have specific questions, please feel free to get in touch.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{6.20 Poem}
Harold Jaffe
\\
Starting Bid: \$1
\newline
SERV Auction returns
I offer humble poems
while leaves keep falling

Add a little lyrical delight to your life! You name the subject(s) and/or theme(s) and/or form, and I will use the power of POETRY to bring it to life. From haiku to sonnets, limericks to spoken word, your options are endless!
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{6.21 The Art of Letter-Writing}
Harold Jaffe
\\
Starting Bid: \$1
\newline
Within one month of the SERV Auction, I will write and send you a handwritten personal letter. If we already know each other, the original letter will tend to be more on the personal side. But even if we haven't had the pleasure of each other's acquaintance, I am sure we will have things to talk about! (And if we are already pen pals and I currently owe you a letter, you could use this to spur me to action.)
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{6.23 Something from Antarctica}
Philip Chung
\\
Starting Bid: \$1
\newline
I'll buy something from one of the stores here in Antarctica that's approximately the value of your bid, and send it to you. Delivery in April 2017.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{6.24 SERV Auction Copy Machine}
Mitch Cieminski
\\
Starting Bid: \$1
\newline
Number of winners: 2
\newline
If you win this item for n dollars, and bid \textless 2n dollars on another item, I will do my best to copy that item as close as I can for you. This may be an exact replica, or something kinda close ish. The copy machine works better on some items than others. One copy per winner.

This item can totally be used as bid insurance (I.e. if you lose an item you still get it), flake insurance (I.e. if you win an item but they never follow through I will instead), or even just item duplication (I.e. you win an item and now you get two of it).
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{6.25 birthday performance}
Annie 
\\
Starting Bid: \$1
\newline
I'll play birthday variations for you on the piano
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{6.32 Pen pal for life}
Graham Hooton ('14)
\\
Starting Bid: \$5
\newline
The winner of this item will receive a mailed letter from me, as well as a mailed letter in reply to any letter that they send me in the future, for life.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{6.33 Phone call on your birthday}
Graham Hooton
\\
Starting Bid: \$5
\newline
I will call you every year on your birthday, for life.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{6.34 Magical Souvenirs}
Michael Sheets
\\
Starting Bid: \$5
\newline
Looking for a little something to remind you of “home”? Missed this year’s ornament and want to complete your set? I’ll be working at Walt Disney World this spring, and will send you a little piece of magic from the parks or resorts during my time there! Your bid will be amount spent on your item(s).
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{6.35 Bring you a Spanish souvenir }
Mackenzie Frackleton
\\
Starting Bid: \$5
\newline
The more donated, the nicer the thing I'll find for you!
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{6.39 Spotify Mix}
Jordyn Burger
\\
Starting Bid: \$5
\newline
Number of winners: 3
\newline
Spotify is my social media of choice. Win this, and I'll make you a killer mix with at least ~20 of my favorite songs. Top three winners will get a jam set!
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{6.40 Write you your own personal theme song!}
Gracey Wilson
\\
Starting Bid: \$5
\newline
Number of winners: 2
\newline
We'll talk, you'll tell me about stuff you like and the optimal way you'd like to be introduced to people. Then I'll write you a jingle for your personal enjoyment!
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{6.43 Sentimental Care Package}
Myles Cooper
\\
Starting Bid: \$7
\newline
Let's face it: you haven't gotten a care package in months, maybe ever. You hear about your friends getting shipments of their favorite food from home and next thing you know you're typing "PACKAGE" into your mail filter just to re-live the experience of seeing an e-mail that's as excited to be read as you are to read it. Well, tell you what: I'll send you a care package. I'll put in it something interesting that I find, or maybe just some stuff I have around that I haven't used in a while and want to get rid of. I may even write you a card making up a story about how it's your favorite. But no matter what, you'll get a care package. Unless the mail loses it or something.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{6.46 Unique/Memorable/Special Gift from Southeast Asia \#1}
Philip Z Loh
\\
Starting Bid: \$10
\newline
Want to get a gift from me from Southeast Asia? I'm traveling all around the area in November (as in right now). Gift scales with winning bid. Gift subject to import restrictions and international law.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{6.47 Special/Memorable/Unique Gift from Southeast Asia \#2}
Philip Z Loh
\\
Starting Bid: \$10
\newline
Want to get a gift from me from Southeast Asia? I'm traveling all around the area in November (as in right now). Gift scales with winning bid. Gift subject to import restrictions and international law.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{6.48 Something Awesome, 10 years from today}
Matt Ritter
\\
Starting Bid: \$10
\newline
On this date, 10 years from today, I will surprise you with something awesome. A silly photo? A retrorickroll? A flying car? Who knows!
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{6.49 Bike ride in San Francisco}
Rachel Bobbins ('12)
\\
Starting Bid: \$10
\newline
I'll take you one one of my favorite bike routes in the SF Bay Area! I'll provide a road bike with your choice of regular or SPD pedals. We can stay in SF, or bike over the Golden Gate Bridge. If you're over 21, we can go to my favorite bar (Gestalt Haus) in Marin and I'll buy you a beer. I know a bunch of flat \& hilly routes, so we can do whatever you're comfortable with. Same deal with distance.

If bidding goes over \$50, you can bring a friend. 
If bidding goes over \$150, you can bring 2 friends. (I have a lot of bikes)
If bidding goes over \$250, we can go bike glamping (I'll rent a cabin at the Petaluma KOA) in Sonoma. Bring up to 4 of your friends, but some of them will have to bring their own bikes.

NOTE: This is probably best for people who are in the 5'2-6'0" range. I have 3 bikes that are suitable for 5'2-5'8"people, and somebody who's taller could borrow Mikey (Lintz, '11)'s bike. 

NOTE: If we keep the ride short (within SF), someone could ALSO ride my folding bike, which is suitable for 4'11" to 5'10"ish people.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{6.51 4 Books Personally Selected for You}
Shane Skikne, Doyung Lee, Kari Bender, Chani Martin, and Forrest Bourke
\\
Starting Bid: \$15
\newline
The four of us have amassed quite a collection of interesting books over the years. Win this item and we'll get to know you a bit (if we don't already) before each choosing a book from our personal collection to give to you. It could be based on your sense of humor, your goals in life, your taste in books or anything else.  Obviously, we'll each write a note in our book to be all cute and stuff (or not, your call).
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{6.53 Rock Climbing Adventure}
Miranda Bethune
\\
Starting Bid: \$20
\newline
Number of winners: 2
\newline
If you're new to rock climbing, I (along with my expert climbing partner) will come pick you up from Olin and take you to our indoor climbing gym, Central Rock Gym in Watertown. We'll take care of your day passes and equipment, and then we'll introduce you to the crazy excellent world of bouldering via your very own climbing lesson. If you're already a climber and you have your own climbing shoes, we'll take you on an outdoor climbing adventure to one of our favorite spots. We can provide the crash pad and snacks, plus transportation to and from Olin. Most importantly: if the bid reaches or surpasses \$100, I will sacrifice my remaining shreds of dignity and climb wearing a giant banana costume.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{6.54 Packages from Cambridge(s)}
Jeff Holzgrafe and Brendan Quinlivan
\\
Starting Bid: \$20
\newline
Want that euphoric experience getting an email from the mailroom saying your package has arrive?? Want it twice, one a bit more local and one from across the pond? Brendan (Cambridge, MA) and Jeff (Cambridge, UK) will each send you a package from their respective cities.  Want proper cadbury's chocolate , bitter marmalade, or a preppy college scarf  from those Europeans with their funny accents?  How about some more local items from Taza chocolate, coffee from 1369, or some homemade cookies/bread? If you win this item, we’ll shoot you an email to check for any dietary restrictions/special requests and we’ll do our best to send you two awesome packages!
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{6.55 Finally, Mitch Gives Something Good}
Mitch Cieminski
\\
Starting Bid: \$20
\newline
In the past, I've won some pretty excellent SERV auction items (like Geoff singing to Oscar whole wearing a speedo, dinner with Rob and Scott, lifetime FWOP tickets, Joshe expressing my opinion, etc). I've also given some pretty solid ones (especially the Needham Pizza Tour 2k16). 

This is an item that could be so much more than any of those. The winter of this item will get a special meeting with me, Mitch Cieminski, in which we discuss my abilities and your needs, and determine the perfect SERV suction item or experience for me to give to you. Then, some time later, you'll get that thing or experience. Sounds simple enough, right? But I personally guarantee that it will be the best SERV auction purchase that you make this year, and possibly ever. This is a big promise, but one that I'm committed to making happen.

The quality of the item will certainly scale with the amount donated. I'm willing to sink my own money into this. Group bids are welcome.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\section*{6.57 Decorate my cast}
Mark Somerville
\\
Starting Bid: \$50
\newline
Mark's wrist is broken.  Soon, he will get a cast.  Under normal circumstances, he would be very protective of said cast, in order to avoid having anything untoward written or drawn thereon.  But SERV is an awfully good cause... 

The winner will also get to keep the cast after it is removed from Mark's arm. No obligation though.
\\[6ex]
\begin{tabular}{c c c}
~~~~~~~~~~~~~Name~~~~~~~~~~~~~ & ~~~~~~~~~Bid (\$)~~~~~~~~~  & ~~~Email Address (if not standard olin.edu)~~~\\
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
 & & \\
\hline
\end{tabular}
\newpage
\end{document}
